---
title: "Results"
author: "Xueming Liu"
date: "`r Sys.Date()`"
output:
  word_document:
    # Enable a table of contents for easy navigation
    toc: true 
    # Limit TOC depth to 2 levels (H1 and H2 headings)
    toc_depth: 2 
    # Optional custom Word template file. Delete this line if you have no template.
    # reference_docx: "custom_styles.docx"
---

```{r}
#rm(list = ls()) # Full wipe: ensure every Run All starts from a clean environment
#graphics.off()  # Close all graphics devices
```


# env set
```{r setup, include=FALSE}
# Set global options

# 1. Load core dependency packages
# Make sure these packages are installed: install.packages(c("mgm", "qgraph", "networktools", "dplyr", "gridExtra", "ggplot2", "missForest"))
library(mgm)
library(qgraph)
library(networktools)
library(dplyr)
library(gridExtra)
library(ggplot2)
library(missForest) # core imputation package
library(bruceR)    # bruceR provides the import() function
library(here)

# ==============================================================================
# Path configuration (edit here; every path below references these)
# ==============================================================================
data_raw_dir   <- here::here('Data', 'Raw')          # raw data (read-only)
data_proc_dir  <- here::here('Data', 'Processed')    # intermediate outputs
out_tables_dir <- here::here('Output', '01-Env-health', 'Tables')
out_fig_dir    <- here::here('Output', '01-Env-health', 'Figures')

# Ensure output directories exist
dir.create(data_proc_dir,  showWarnings = FALSE, recursive = TRUE)
dir.create(out_tables_dir, showWarnings = FALSE, recursive = TRUE)
dir.create(out_fig_dir,    showWarnings = FALSE, recursive = TRUE)

```




```{r}
# ==============================================================================
# Step 1: Data loading and preprocessing (safe version + CSV export)
# ==============================================================================

# 1. Define mapping values
livnum_values <- c(1, 2, 3, 4, 5, 6, 7.5)  
livarea_values <- c(75, 175, 225, 275, 325, 375, 425, 475, 575, 675, 775, 825, 875, 975, 1100) 

# 2. Define new column names (97 variables)
new_colnames <- c(
  "e_city","e_dist","e_metro","e_Bus","e_wlkgrn","e_wvgrn","e_wlkblu", "e_wvblu","e_facil","e_Price","e_work","e_eduEL","e_comCen","e_medAc","e_alcig","e_neiAl","e_neiLow","e_neiSoci","e_themCo","e_clim","e_poll","e_lighting","e_privacy","e_narrow","e_PA","e_sleep","e_heaFood","e_lifestyle","e_safe",
  "greenden","greennat","greendis" ,"greenfreq","greendura",
  "blueden","bluenat","bluedis","bluefreq","bluedura",
  'l_palgt','l_pamed','l_pahig','l_lgtdur','l_meddur','l_higdur','l_sitdur','l_leidur',"l_eathealth",'l_eatout','l_smoking','l_drinking',"l_medictest","l_adaptCop", "l_med_seek","l_info_seek", 
  "m_conc","m_wea","m_pos","m_app","m_neg","m_est","m_res","m_eat",
  "p_energy","p_pain","p_medD","p_genH","p_sleep","p_daily","p_work","p_mobility",
  "SC_1","SC_2" ,"SC_3" ,"SC_4","SC_5",
  "SS_1","SS_2","SS_3","SS_4","SS_5","SS_6","SS_7","SS_8",
  "TBPB_1","TBPB_2","TBPB_3","TBPB_4","TBPB_5","TBPB_6","TBPB_7" ,"TBPB_8" ,"TBPB_9","TBPB_10",
  'Pain tolerance', 'Fearless of death', "suicide idea","suicide plan","suicide attempt","Smean",
  "SN_1","SN_2","SN_3","SN_4","SN_5","SN_6","SN_7","SN_8","SN_9",
  "Age", "Gender", "Edu", "Emp", "Imm", "CD", "DurRes", "LivArea", 
  "i_thwBelong", "i_perBurden", "i_acqCapability",
  "Mental" ,"Physical","Social"
)

# 3. Build a temporary data frame (df_temp) -- without setNames
df_temp <- bruceR::import(here::here('Data', 'Raw', 'merged_data0925.xlsx')) %>% 
  dplyr::select('disU','disD',
         'disMTR',
         'disBus',
         'diverFa',
         'Price',
         'eduE',
         'eduL',
         'comCen',
         'medAc',
         'walkG',
         'walkB',
         'neiAlo',
         'neiLow',
         'lowFa',
         'neisocial', 
         'themCo_R', 
         'clim_R',
         'conta',
         'light_R', 
         'privacy_R',
         'narrow',
         'winG',
         'winB',
         'lessWork',
         'alcohol',
         'cigarette',
         'lowPhysi',
         'sleep_R',
         'heaFood_R',
         'lifestyle_R',
         'unsafe',
         'greenden',
         'greennat',
         'greendis',
         'greenfreq',
         'greendura',
         'blueden',
         'bluenat',
         'bluedis',
         'bluefreq',
         'bluedura',
          'conc', 'wea', 'pos', 'app', 'neg', 'est', 'res', 'eat', 
          "energy", "pain", "medD", "genH", "sleep", "daily", "work", "mobility",
          'SNAa_1','SNAa_2','SNAa_3','SNAa_4','SNAa_5','SNAa_6','SNAa_7','SNAa_8','SNAa_9',
          'SNBa_1','SNBa_2','SNBa_3','SNBa_4','SNBa_5','SNBa_6','SNBa_7','SNBa_8','SNBa_9',
          'SC_1','SC_2','SC_3','SC_4','SC_5',
          'SS_1','SS_2','SS_3','SS_4','SS_5','SS_6','SS_7','SS_8',
          'AC_3','AC_4', 'AC_5',
          'TBPB_1','TBPB_2',	'TBPB_3',	'TBPB_4'	,'TBPB_5'	,
          'TBPB_6',	'TBPB_7',	'TBPB_8',	'TBPB_9',	'TBPB_10',
          'AC_1','AC_2',
          # SES
          'age', 'gender', 'edu', 'emp', 'imm','disease',
          # 'indinco',
          'liviDura','livnum','livarea',
          # added variables
          'SC_96', 'SC_104', 'SC_103', 'SC_99', 'SC_105', 'SC_20',  'RMT_20', 'RMT_80', 'RMT_81', 'RMT_82', 'RMT_83', 'RMT_84','HIT_36' ,'HIT_37' , 'HIT_4',
          # health behavior
          'LF','MF','HF','AP_1','AP_2','AP_3','SP','LAF','HD_1','HD_2','HD_3','HD_4','OE','Sm','Dri',"RM"
  ) %>%
  dplyr::mutate(
    livnum_val = livnum_values[as.numeric(livnum)],   
    livarea_val = livarea_values[as.numeric(livarea)]  
  ) %>%
  dplyr::mutate( 
    eduEL = (eduE + eduL) /2,
    Smean = (AC_3 + AC_4 + AC_5) / 3,
    SN_1 = (SNAa_1 + SNBa_1) / 2,
    SN_2 = (SNAa_2 + SNBa_2) / 2,
    SN_3 = (SNAa_3 + SNBa_3) / 2,
    SN_4 = (SNAa_4 + SNBa_4) / 2,
    SN_5 = (SNAa_5 + SNBa_5) / 2,
    SN_6 = (SNAa_6 + SNBa_6) / 2,
    SN_7 = (SNAa_7 + SNBa_7) / 2,
    SN_8 = (SNAa_8 + SNBa_8) / 2,
    SN_9 = (SNAa_9 + SNBa_9) / 2,
    livareaperson = livarea_val / livnum_val
  ) %>%
  dplyr::mutate(
    TB = (TBPB_1 + TBPB_2 + TBPB_3 + TBPB_4 + TBPB_5)/5,
    PB = ((6-TBPB_6) + (6-TBPB_7) + TBPB_8 + TBPB_9 + (6-TBPB_10))/5,
    AC = ((6-AC_1)+AC_2)/2
  ) %>%
  dplyr::select(-starts_with("SNAa_"), -starts_with("SNBa_")) %>%
  dplyr::mutate(disease = ifelse(disease == "1", 1, 0)) %>%
  dplyr::filter(gender %in% c(1, 2)) %>% 
  dplyr::mutate(
    liviDura = case_when(
      liviDura == "1-2 年" ~ 1,
      liviDura == "2-3 年" ~ 1,
      liviDura == "3-4 年" ~ 1,
      liviDura == "4-5 年" ~ 1,
      liviDura == "5-6年" ~ 2,
      liviDura == "6-7年" ~ 2,
      liviDura == "7-8年" ~ 2,
      liviDura == "8-9年" ~ 2,
      liviDura == "9-10年" ~ 2,
      liviDura == "10-11年" ~ 3,
      liviDura == "11-12年" ~ 3,
      liviDura == "12-13年" ~ 3,
      liviDura == "13-14年" ~ 3,
      liviDura == "14-15年" ~ 3,
      liviDura == "15-16年" ~ 4,
      liviDura == "16-17年" ~ 4,
      liviDura == "17-18年" ~ 4,
      liviDura == "18-19年" ~ 4,
      liviDura == "19-20年" ~ 4,
      liviDura == "超過20年" ~ 5,
      TRUE ~ NA_real_ 
    )
  ) %>%
  dplyr::mutate(edu=as.numeric(edu)) %>%
  # Compute map_SC and health literacy
  mutate(across(c('SC_96', 'SC_104', 'SC_103', 'SC_99', 'SC_105', 'SC_20'), ~tidyr::replace_na(., 0))) %>%
  mutate(l_adaptCop_raw = SC_96 + SC_104 + SC_103 + SC_99 + SC_105 + SC_20) %>%
  mutate(across(c(RMT_20, RMT_80, RMT_81, RMT_82, RMT_83, RMT_84), ~tidyr::replace_na(., 0))) %>%
  mutate(l_med_seek = if_else((RMT_20 + RMT_80 + RMT_81 + RMT_82 + RMT_83 + RMT_84) > 0, 1, 0)) %>%
  mutate(across(c(HIT_36, HIT_37, HIT_4), ~tidyr::replace_na(., 0))) %>%
  mutate(l_info_seek = HIT_36 + HIT_37 + HIT_4) %>%
  
  dplyr::mutate(
    HDietmean = rowMeans(dplyr::select(.,'HD_1', 'HD_2', 'HD_3', 'HD_4'),na.rm = TRUE),
    mehmean = rowMeans(dplyr::select(.,'conc', 'wea', 'pos', 'app', 'neg', 'est', 'res', 'eat'),na.rm = TRUE),
    pyhmean = rowMeans(dplyr::select(.,"energy", "pain", "medD", "genH", "sleep", "daily", "work", "mobility"),na.rm = TRUE),
    sohmean = rowMeans(dplyr::select(.,'SN_1','SN_2','SN_3','SN_4','SN_5','SN_6','SN_7','SN_8','SN_9','SC_1','SC_2','SC_3','SC_4','SC_5','SS_1','SS_2','SS_3','SS_4','SS_5','SS_6','SS_7','SS_8'), na.rm = TRUE)
  ) %>%
  mutate(
    e_alcig_R = 6-(alcohol+cigarette)/2,
    Work_R  = 6 - lessWork,
    safe_R  = 6 - unsafe,
    facil  = (diverFa + (6-lowFa)) / 2,
    neiAlo_R = 6 - neiAlo,
    neiLow_R = 6 - neiLow,
    PA  =  lowPhysi,
    conta_R = 6 - conta,
    narrow_R = 6 - narrow,
    SP_R = 14 - SP,
    OE_R = 8 - OE,
    Sm_R = 10 - Sm,
    Dri_R = 10 - Dri,
    neg_R = 6 - neg,
    pain_R = 6 - pain,
    medD_R = 6 - medD
  ) %>%
  dplyr::select(-livarea,-livnum, -livarea_val, -livnum_val,
                -HD_1,-HD_2,-HD_3,-HD_4,-lessWork,-unsafe,-diverFa, -lowFa,-lowPhysi) %>%
  # Final selection (order and count must match new_colnames)
  dplyr::select("disU","disD","disMTR","disBus","walkG","winG","walkB","winB","facil","Price","Work_R", "eduEL","comCen","medAc","e_alcig_R","neiAlo_R","neiLow_R","neisocial","themCo_R","clim_R","conta_R","light_R","privacy_R","narrow_R","PA","sleep_R","heaFood_R","lifestyle_R","safe_R",
                "greenden","greennat","greendis" ,"greenfreq","greendura",
                "blueden","bluenat","bluedis","bluefreq","bluedura",
                "LF","MF","HF","AP_1","AP_2","AP_3","SP_R","LAF","HDietmean","OE","Sm","Dri","RM","l_adaptCop_raw","l_med_seek","l_info_seek",
                "conc","wea","pos","app","neg_R","est","res","eat",
                "energy","pain_R","medD_R","genH","sleep","daily","work","mobility",
                "SC_1","SC_2" ,"SC_3" ,"SC_4","SC_5",
                "SS_1","SS_2","SS_3","SS_4","SS_5","SS_6","SS_7","SS_8",
                "TBPB_1","TBPB_2","TBPB_3","TBPB_4","TBPB_5","TBPB_6","TBPB_7" ,"TBPB_8" ,"TBPB_9","TBPB_10",
                "AC_1","AC_2", "AC_3","AC_4","AC_5","Smean",
                "SN_1","SN_2","SN_3","SN_4","SN_5","SN_6","SN_7","SN_8","SN_9",
                "age","gender","edu","emp","imm","disease","liviDura","livareaperson",
                "TB","PB","AC",
                "mehmean" ,"pyhmean","sohmean" ) %>%
  mutate(
    age     = as.numeric(age),
    gender  = factor(gender),
    edu     = factor(edu, ordered = TRUE), 
    emp     = factor(emp),
    imm     = factor(imm),
    disease = factor(disease),
    liviDura = as.numeric(liviDura),
    livareaperson = as.numeric(livareaperson)
  )

# --- 4. Run safety check ---
current_cols <- ncol(df_temp)
target_cols <- length(new_colnames)

if(current_cols != target_cols) {
  msg <- paste0(
    "Column count mismatch!\n",
    "------------------------------\n",
    "Current number of columns: ", current_cols, "\n",
    "Number of new variable names: ", target_cols, "\n",
    "Difference: ", current_cols - target_cols, "\n",
    "------------------------------\n",
    "Check whether the select() statement is missing variables, or new_colnames is defined incorrectly."
  )
  stop(msg)
} else {
  message("Column count check passed (", current_cols, " vs ", target_cols, ").")
  
  # --- 5. Safe rename ---
  df <- df_temp %>% setNames(new_colnames)
  message("Data frame df created and renamed successfully.")
  
  # --- 6. Export CSV ---
  write.csv(df, file.path(data_proc_dir, "data_cleaned_step1.csv"), row.names = FALSE, fileEncoding = "UTF-8")
  message("CSV exported: data_cleaned_step1.csv")
}

# Report overall missingness
cat("\nOverall missingness of the data frame:\n")
print(skimr::skim(df))
```


# Data input
```{r}
# ==============================================================================
# Step 1: Variable definition, selection and renaming
# ==============================================================================
library(dplyr)
library(missForest)
library(psych)
library(tibble)

# 1.1 Define original variable names (list kept as provided)
e_orig_names <- c("e_city", "e_dist", "e_metro", "e_Bus", "e_wlkgrn", "e_wvgrn", "e_wlkblu", "e_wvblu",
                  "e_facil", "e_Price", "e_work", "e_eduEL", "e_comCen", "e_medAc", "e_alcig", 
                  "e_neiAl", "e_neiLow", "e_neiSoci", "e_themCo", "e_clim", "e_poll", "e_lighting",
                  "e_privacy", "e_narrow", "e_PA", "e_sleep", "e_heaFood", "e_lifestyle", "e_safe")

l_orig_names <- c('l_palgt', 'l_pamed', 'l_pahig', 'l_lgtdur', 'l_meddur', 'l_higdur', 
                  'l_sitdur', 'l_leidur', "l_eathealth", 'l_eatout', 'l_smoking', 
                  'l_drinking', "l_medictest", "l_adaptCop", "l_med_seek", "l_info_seek")

mh_orig_names <- c('m_conc', 'm_wea', 'm_pos', 'm_app', 'm_neg', 'm_est', 'm_res', 'm_eat')
ph_orig_names <- c("p_energy","p_pain","p_medD","p_genH","p_sleep","p_daily","p_work","p_mobility")
sh_orig_names <- c("SS_1","SS_2","SS_3","SS_4","SS_5","SS_6","SS_7","SS_8")
ses_vars <- c("Age", "Gender", "Edu", "Emp", "Imm", "CD", "DurRes", "LivArea")

# 1.2 Select data
all_vars_for_imputation <- c(e_orig_names, l_orig_names, mh_orig_names, ph_orig_names, sh_orig_names, ses_vars)

# Check that the variables exist
if(!all(all_vars_for_imputation %in% colnames(df))) {
  missing_vars <- all_vars_for_imputation[!all_vars_for_imputation %in% colnames(df)]
  stop(paste("Error: the data frame is missing the following columns:", paste(missing_vars, collapse=", ")))
}

df_analysis <- df[, all_vars_for_imputation]

# 1.3 Rename (build old-to-new name mapping)
# Generate new names
e_item_names <- paste0("E", 1:length(e_orig_names))
l_item_names <- paste0("L", 1:length(l_orig_names))
mh_item_names <- paste0("M", 1:length(mh_orig_names))
ph_item_names <- paste0("P", 1:length(ph_orig_names))
sh_item_names <- paste0("S", 1:length(sh_orig_names))

# Apply the renaming
names(df_analysis)[match(e_orig_names, names(df_analysis))] <- e_item_names
names(df_analysis)[match(l_orig_names, names(df_analysis))] <- l_item_names
names(df_analysis)[match(mh_orig_names, names(df_analysis))] <- mh_item_names
names(df_analysis)[match(ph_orig_names, names(df_analysis))] <- ph_item_names
names(df_analysis)[match(sh_orig_names, names(df_analysis))] <- sh_item_names

# Reorder (E, L, M, P, S, SES)
core_node_names <- c(e_item_names, l_item_names, mh_item_names, ph_item_names, sh_item_names)
all_vars_clean <- c(core_node_names, ses_vars)
df_analysis <- df_analysis[, all_vars_clean]

message("Variable selection and renaming complete.")

# ==============================================================================
# Step 2: Descriptive statistics of the raw data (pre-imputation)
# ==============================================================================

# Define a generic descriptive-statistics function
get_descriptive_stats <- function(data, label="Stats") {
  
  data_num <- data %>% mutate(across(everything(), ~as.numeric(.)))
  
  # Use psych::describe for basic statistics
  desc <- psych::describe(data_num, na.rm = TRUE) %>%
    as.data.frame() %>%
    rownames_to_column("Variable") %>%
    dplyr::select(Variable, mean, sd, min, max, skew)
  
  missing_counts <- sapply(data, function(x) sum(is.na(x)))
  var_types <- sapply(data, function(x) class(x)[1])
  
  # Merge
  final_tab <- desc %>%
    mutate(
      Missing_N = missing_counts[Variable],
      Missing_Pct = round(Missing_N / nrow(data) * 100, 2),
      Type = var_types[Variable]
    ) %>%
    mutate(across(c(mean, sd, skew), ~round(., 3))) # keep 3 decimal places
  
  return(final_tab)
}

# 2.1 Ensure SES variables have the right format (for statistics)
ses_factor_vars <- c("Gender", "Emp", "Imm", "CD", "Edu")
df_raw_stat <- df_analysis
for(col in ses_factor_vars) {
  if(col %in% names(df_raw_stat)) df_raw_stat[[col]] <- as.factor(df_raw_stat[[col]])
}

# 2.2 Build and export the raw statistics table
stats_raw <- get_descriptive_stats(df_raw_stat)

# Export CSV
write.csv(stats_raw, file.path(out_tables_dir, "Table_Descriptive_Raw_Data.csv"), row.names = FALSE)
message("Raw-data statistics table exported: Table_Descriptive_Raw_Data.csv")

# Print a preview (first few rows)
print(head(stats_raw))

# ==============================================================================
# Step 3: missForest imputation
# ==============================================================================

# 3.1 Prepare data for imputation (categorical variables must be factors)
df_for_imp <- df_analysis
for(col in ses_factor_vars) {
  df_for_imp[[col]] <- as.factor(df_for_imp[[col]])
}

message("\nStarting missForest imputation (ntree=500)... this may take a few minutes...")

# 3.2 Run the imputation
set.seed(123) # fix the random seed for reproducibility
imp_result <- missForest(df_for_imp, 
                         verbose = TRUE, 
                         ntree = 500,     
                         maxiter = 10)

# Extract the imputed data
df_clean <- imp_result$ximp

# 3.3 Print the error report
message("\nImputation complete. OOB error estimate:")
print(imp_result$OOBerror)

# ==============================================================================
# Step 4: Pre/post-imputation comparison report
# ==============================================================================

# 4.1 Build the post-imputation statistics table
stats_imp <- get_descriptive_stats(df_clean)

# 4.2 Merge for comparison
comparison_table <- stats_raw %>%
  dplyr::select(Variable, Raw_Mean = mean, Raw_SD = sd, Raw_Skew = skew, Missing_N) %>%
  left_join(
    stats_imp %>% dplyr::select(Variable, Imp_Mean = mean, Imp_SD = sd, Imp_Skew = skew),
    by = "Variable"
  ) %>%
  mutate(
    Mean_Diff = round(Imp_Mean - Raw_Mean, 4),
    SD_Diff = round(Imp_SD - Raw_SD, 4)
  )

# 4.3 Export the comparison table
write.csv(comparison_table, file.path(out_tables_dir, "Table_Imputation_Check.csv"), row.names = FALSE)
message("Pre/post-imputation comparison table exported: Table_Imputation_Check.csv")

# 4.4 Check for large changes (warn if a mean shifts by more than 0.5)
large_changes <- comparison_table %>% filter(abs(Mean_Diff) > 0.5)
if(nrow(large_changes) > 0) {
  message("Warning: the following variables show a large mean change after imputation, please check:")
  print(large_changes$Variable)
} else {
  message("Check passed: no large mean shift between pre- and post-imputation.")
}

# ==============================================================================
# Step 5: Final output (prepare for the next splitting step)
# ==============================================================================

for(col in colnames(df_clean)) {
  if(is.factor(df_clean[[col]])) {
    df_clean[[col]] <- as.numeric(as.character(df_clean[[col]]))
    if(any(is.na(df_clean))) stop("Numeric conversion introduced NA")
  }
}

message("\nReady. df_clean is now a complete numeric data frame with no missing values.")
message("Continue with the Step 4 (data splitting) code.")
```


# advanced data process-df_clean
```{r}
# ==============================================================================
# Step 4: Data forking (SES dummy-variable control, fixed)
# ==============================================================================
# Key correction:

library(dplyr)
library(tidyr)

message("\n[Step 4] Running data forking (SES type-corrected version)...")

# --- 1. Variable definitions ---

all_items <- c(e_item_names, l_item_names, mh_item_names, ph_item_names, sh_item_names)
ses_vars <- c("Age", "Gender", "Edu", "Emp", "Imm", "CD", "DurRes", "LivArea")

# Group A: treated as continuous numeric (includes low-to-high ordinal variables such as Edu)
ses_numeric_vars <- c("Age", "Edu", "DurRes", "LivArea") 

# Group B: must be treated as categorical factors (nominal + binary variables)
ses_factor_vars <- c("Gender", "Emp", "Imm", "CD")

# --- 2. Prepare the SES data frame (for lm regression) ---

ses_df_model <- df_clean %>%
  dplyr::select(all_of(ses_vars)) %>%
  mutate(across(all_of(ses_numeric_vars), ~as.numeric(as.character(.)))) %>%
  mutate(across(all_of(ses_factor_vars), ~as.factor(.)))

str(ses_df_model)

# --- 3. Prepare the item data ---
df_clean_num <- as.data.frame(df_clean) %>%
  mutate(across(all_of(all_items), ~as.numeric(as.character(.))))


# --- 4. Run the forking ---

# === Branch A: df_raw_bggm (for BGGM) ===
df_raw_bggm <- df_clean_num 
message("df_raw_bggm ready.")


# === Branch B: df_resid (for DAG) ===
df_resid <- df_clean_num # copy the structure

message("Computing residuals (dummies handled automatically)...")

for(item in all_items) {
  tmp_data <- cbind(Y_Target = df_clean_num[[item]], ses_df_model)
  
  fit <- lm(Y_Target ~ ., data = tmp_data, na.action = na.exclude)
  
  df_resid[[item]] <- residuals(fit)
}

message("df_resid ready (SES categorical variables correctly controlled).")


# --- 5. Compute composite scores ---
calc_score <- function(data, vars) {
  if(length(vars) == 0) return(rep(NA, nrow(data)))
  rowMeans(data[, vars, drop=FALSE], na.rm=TRUE)
}

df_scores <- df_resid %>%
  mutate(
    E_Score = calc_score(., e_item_names),
    L_Score = calc_score(., l_item_names),
    M_Score = calc_score(., mh_item_names),
    P_Score = calc_score(., ph_item_names),
    S_Score = calc_score(., sh_item_names),
    H_Score_Total = rowMeans(cbind(M_Score, P_Score, S_Score), na.rm=TRUE)
  ) %>%
  mutate(across(c(E_Score, L_Score, M_Score, P_Score, S_Score, H_Score_Total), ~as.numeric(scale(.))))

message("df_scores ready.")

# ==============================================================================
# Save
# ==============================================================================
continuous_items <- c() 

save(df_clean_num, df_raw_bggm, df_resid, df_scores, 
     ses_df_model,
     continuous_items,
     file = file.path(data_proc_dir, "Data_Forked_Step4.RData"))

message("\nData updated and saved to Data_Forked_Step4.RData")


```


# Analysis 1: z-scoring, correlation and mediation test
```{r}
# ==============================================================================
# Step 5A: Composite-score z-score descriptive statistics (select-conflict fix)
# ==============================================================================
library(dplyr)
library(tidyr)
library(openxlsx)
library(ggplot2)
library(patchwork)

# Ensure df_scores exists
if(!exists("df_scores")) stop("Error: df_scores does not exist. Run the Step 4 code first.")

message("\n[Step 5A] Computing z-score descriptive statistics...")

# 1. Define the score variables to analyse
score_names <- c("E_Score", "L_Score", "M_Score", "P_Score", "S_Score", "H_Score_Total")

# 2. Build the descriptive-statistics table
desc_scores <- df_scores %>%
  dplyr::select(all_of(score_names)) %>%
  summarise(across(everything(), list(
    Mean = ~mean(.x, na.rm = TRUE), 
    SD = ~sd(.x, na.rm = TRUE),
    Min = ~min(.x, na.rm = TRUE), 
    Max = ~max(.x, na.rm = TRUE),
    Skew = ~moments::skewness(.x, na.rm = TRUE)
  ), .names = "{.col}_{.fn}")) %>%
  pivot_longer(everything(), names_to = c("Index", "Statistic"), 
               names_pattern = "(.*)_(.*)", values_to = "Value") %>%
  pivot_wider(names_from = Statistic, values_from = Value) %>%
  mutate(Description = case_when(
    Index == "E_Score" ~ "Environment (Residuals Z-score)",
    Index == "L_Score" ~ "Lifestyle (Residuals Z-score)",
    Index == "M_Score" ~ "Mental Health (Residuals Z-score)",
    Index == "P_Score" ~ "Physical Health (Residuals Z-score)",
    Index == "S_Score" ~ "Social Health (Residuals Z-score)",
    Index == "H_Score_Total" ~ "Overall Health (Mean of M+P+S)",
    TRUE ~ Index
  )) %>%
  dplyr::select(Index, Description, Mean, SD, Skew, Min, Max) %>%
  mutate(across(where(is.numeric), ~round(., 3)))

print(desc_scores)

# 3. Export to Excel
wb <- createWorkbook()
addWorksheet(wb, "Scores_Z_Stats")
writeData(wb, "Scores_Z_Stats", desc_scores)
setColWidths(wb, "Scores_Z_Stats", cols = 1:7, widths = 15)
saveWorkbook(wb, file.path(out_tables_dir, "Table_Scores_Descriptive.xlsx"), overwrite = TRUE)

# 4. Draw the density-distribution plot (appendix)
plot_data <- df_scores %>%
  dplyr::select(all_of(score_names)) %>%
  pivot_longer(everything(), names_to = "Dimension", values_to = "Score")

p_dist <- ggplot(plot_data, aes(x = Score, fill = Dimension)) +
  geom_density(alpha = 0.5) +
  geom_vline(xintercept = 0, linetype="dashed", color="gray40") +
  facet_wrap(~Dimension, scales = "free") +
  theme_minimal() +
  labs(title = "Distribution of Standardized Residual Scores",
       subtitle = "Data: SES-controlled Residuals",
       x = "Z-score", y = "Density") +
  theme(legend.position = "none")

ggsave(file.path(out_fig_dir, "Appendix_Score_Distribution.png"), p_dist, width = 10, height = 6)
message("Descriptive statistics done.")

# ==============================================================================
# Step 5B: Correlation analysis (Spearman) - select-error fix
# ==============================================================================

library(psych)
library(corrplot)
library(reshape2)
library(dplyr) # make sure it is loaded

message("\n[Step 5B] Running the correlation analysis...")

# 1. Prepare data
vars_corr <- c("E_Score", "L_Score", "H_Score_Total", "M_Score", "P_Score", "S_Score")

# Fix: use dplyr::select explicitly to avoid an error
df_corr <- df_scores %>% 
  dplyr::select(all_of(vars_corr))

# 2. Compute the Spearman correlation matrix
cor_res <- psych::corr.test(df_corr, method = "spearman", adjust = "none")
r_mat <- cor_res$r
p_mat <- cor_res$p

# 3. Draw the heatmap with significance stars (standard academic style)
melt_r <- melt(r_mat)
melt_p <- melt(p_mat)

plot_df <- left_join(melt_r, melt_p, by = c("Var1", "Var2")) %>%
  rename(Correlation = value.x, P_Value = value.y) %>%
  mutate(
    # Build the significance-star label
    Stars = case_when(
      P_Value < 0.001 ~ "***",
      P_Value < 0.01  ~ "**",
      P_Value < 0.05  ~ "*",
      TRUE ~ ""
    ),
    Label = paste0(sprintf("%.2f", Correlation), "\n", Stars)
  )

# Plot
p_corr <- ggplot(plot_df, aes(Var1, Var2, fill = Correlation)) +
  geom_tile(color = "white") +
  geom_text(aes(label = Label), size = 3) +
  scale_fill_gradient2(low = "#6D9EC1", high = "#E46726", mid = "white", 
                       midpoint = 0, limit = c(-1, 1), name="Spearman\nCorrelation") +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  coord_fixed() +
  labs(title = "Correlation Matrix (SES-Adjusted Scores)", x = "", y = "")

ggsave(file.path(out_fig_dir, "Figure_Correlation_Heatmap.pdf"), p_corr, width = 8, height = 7)
message("Correlation heatmap saved: Figure_Correlation_Heatmap.pdf")


# ==============================================================================
# Step 5C: Mediation analysis (result extraction - select-error fix)
# ==============================================================================
library(lavaan)
library(dplyr)

message("\n[Step 5C] Running the mediation analysis (lavaan)...")

# 1. Define the function
run_mediation <- function(data, outcome_var, label) {
  model <- paste0('
    L_Score ~ a * E_Score
    ', outcome_var, ' ~ b * L_Score + c_prime * E_Score
    indirect := a * b
    total    := c_prime + (a * b)
    pm       := indirect / total
  ')
  
  set.seed(1234) 
  fit <- sem(model, data = data, se = "bootstrap", bootstrap = 5000)
  return(list(fit = fit, label = label, outcome = outcome_var))
}

# 2. Run in batch and extract the results
med_models <- list()
outcomes <- list(
  "Total_Health"    = "H_Score_Total",
  "Mental_Health"   = "M_Score",
  "Physical_Health" = "P_Score",
  "Social_Health"   = "S_Score"
)

summary_list <- list()

for(name in names(outcomes)) {
  message(paste("   ⏳ Running model:", name))
  
  res <- run_mediation(df_scores, outcomes[[name]], name)
  med_models[[name]] <- res 
  
  # --- Result extraction (error-fixed) ---
  est <- parameterEstimates(res$fit, standardized = TRUE, boot.ci.type = "perc") %>%
    as.data.frame() %>%
    
    dplyr::filter(label %in% c("a", "b", "c_prime", "indirect", "total", "pm")) %>%
    
    dplyr::mutate(
      Path_Label = case_when(
        label == "a" ~ "Environment -> Lifestyle",
        label == "b" ~ paste0("Lifestyle -> ", name),
        label == "c_prime" ~ paste0("Environment -> ", name, " (Direct)"),
        label == "indirect" ~ paste0("Env -> Life -> ", name, " (Mediation)"),
        label == "total" ~ paste0("Environment -> ", name, " (Total)"),
        label == "pm" ~ "% Mediation",
        TRUE ~ NA_character_
      )
    ) %>%
    
    dplyr::mutate(
      CI_Str = paste0("[", sprintf("%.3f", ci.lower), ", ", sprintf("%.3f", ci.upper), "]")
    ) %>%
    
    dplyr::select(
      Model = rhs, # temporary placeholder
      `Path / Effect` = label,
      `Path Label` = Path_Label,
      `Standardized Coefficient (β)` = std.all,
      `Standard Error (SE)` = se,
      `P` = pvalue,
      `95% CI (Bootstrap)` = CI_Str
    ) %>%
    
    dplyr::mutate(
      Model = name,
      `Standardized Coefficient (β)` = round(`Standardized Coefficient (β)`, 3),
      `Standard Error (SE)` = round(`Standard Error (SE)`, 3),
      `P` = sprintf("%.3f", `P`)
    )
  
  summary_list[[name]] <- est
}

# 3. Combine and export
final_med_tab <- bind_rows(summary_list)

print(head(final_med_tab))

write.csv(final_med_tab, file.path(out_tables_dir, "Table_Mediation_Results_Final_Beta.csv"), row.names = FALSE, fileEncoding = "UTF-8")
message("Results exported: Table_Mediation_Results_Final_Beta.csv")

```



```{r}
# ==============================================================================
# Step 5D: Mediation-model visualisation (with residual arrows)
# ==============================================================================
library(ggplot2)
library(dplyr)
library(tidyr)
library(stringr)
library(patchwork)

message("\n[Step 5D] Building the mediation-model visualisation (with residual arrows)...")

# Inspect the data structure of the Total_Health model
message("Printout of the model results below:")
print(summary_list[["Total_Health"]])

# 1. Extract path coefficients from the results (unchanged)
extract_path_coefficients <- function(model_name) {
  model_data <- summary_list[[model_name]]
  
  paths <- data.frame(
    from = c("E_Score", "L_Score", "E_Score"),
    to = c("L_Score", model_name, model_name),
    path_type = c("E→L", "L→Y", "E→Y"),
    beta = c(
      model_data %>% filter(`Path / Effect` == "a") %>% pull(`Standardized Coefficient (β)`),
      model_data %>% filter(`Path / Effect` == "b") %>% pull(`Standardized Coefficient (β)`),
      model_data %>% filter(`Path / Effect` == "c_prime") %>% pull(`Standardized Coefficient (β)`)
    ),
    p_value = c(
      model_data %>% filter(`Path / Effect` == "a") %>% pull(P) %>% as.numeric(),
      model_data %>% filter(`Path / Effect` == "b") %>% pull(P) %>% as.numeric(),
      model_data %>% filter(`Path / Effect` == "c_prime") %>% pull(P) %>% as.numeric()
    )
  )
  
  paths$label <- sprintf("β = %.3f%s", 
                         paths$beta,
                         ifelse(paths$p_value < 0.001, "***",
                                ifelse(paths$p_value < 0.01, "**",
                                       ifelse(paths$p_value < 0.05, "*", ""))))
  return(paths)
}

# 2. Function to draw the mediation-model diagram (auto-computes residuals)
plot_mediation_model <- function(model_name, title_suffix = "") {
  
  model_data <- summary_list[[model_name]]
  
  # -------------------------------------------------------
  # -------------------------------------------------------
  paths <- extract_path_coefficients(model_name)
  
  # -------------------------------------------------------
  # B. Auto-compute residual / unexplained variance
  # -------------------------------------------------------
  
  # 1. Extract the coefficient values
  beta_a <- paths %>% filter(path_type == "E→L") %>% pull(beta)
  beta_b <- paths %>% filter(path_type == "L→Y") %>% pull(beta)
  beta_c_prime <- paths %>% filter(path_type == "E→Y") %>% pull(beta)
  
  # 2. Compute the residual for the mediator (Lifestyle)
  # Formula: Var(L) = beta_a^2 * Var(E) + Var(e_L) => 1 = beta_a^2 + e^2
  r2_med <- beta_a^2
  e_med <- sqrt(max(0, 1 - r2_med)) # max(0,...) guards against a negative from float error
  
  # 3. Compute the residual for the outcome (Health)
  # Formula: Var(Y) = Explained_Var + Var(e_Y)
  # Explained_Var = beta_c'^2 + beta_b^2 + 2 * beta_c' * beta_b * correlation(E,L)
  r2_out <- beta_c_prime^2 + beta_b^2 + (2 * beta_c_prime * beta_b * beta_a)
  e_out <- sqrt(max(0, 1 - r2_out))
  
  message(paste0("   [auto] ", model_name, 
                 " | R2_Med=", round(r2_med,3), " (e=", round(e_med,2), ")",
                 " | R2_Out=", round(r2_out,3), " (e=", round(e_out,2), ")"))

  # -------------------------------------------------------
  # C. Define residual-arrow positions
  # -------------------------------------------------------
  error_data <- data.frame(
    name = c("Lifestyle", get_friendly_name(model_name)),
    x_start = c(2.9, 2.9),  # arrow start
    x_end   = c(2.4, 2.4),  # arrow end (touching the box edge)
    y       = c(2, 1),      # same height as the nodes
    label   = c(sprintf("%.2f", e_med), sprintf("%.2f", e_out))
  )
  
  # -------------------------------------------------------
  # D. Set node positions
  # -------------------------------------------------------
  nodes <- data.frame(
    name = c("Environment", "Lifestyle", get_friendly_name(model_name)),
    x = c(1, 2, 2),
    y = c(2, 2, 1)
  )
  
  edges <- data.frame(
    from = c("Environment", "Lifestyle", "Environment"),
    to = c("Lifestyle", get_friendly_name(model_name), get_friendly_name(model_name)),
    beta = paths$beta,
    path_type = paths$path_type,
    label = paths$label
  ) %>%
    left_join(nodes, by = c("from" = "name")) %>%
    rename(x_start = x, y_start = y) %>%
    left_join(nodes, by = c("to" = "name")) %>%
    rename(x_end = x, y_end = y)
  
  color_mapping <- c("E→L"="#87CEEB", "L→Y"="#FFB6C1", "E→Y"="#90EE90")
  edges$linewidth <- abs(edges$beta) * 5
  
  # -------------------------------------------------------
  # E. Plot (ggplot2)
  # -------------------------------------------------------
  p <- ggplot() +
    # 1. Draw the node boxes
    geom_rect(data = nodes, 
              aes(xmin = x - 0.4, xmax = x + 0.4, 
                  ymin = y - 0.15, ymax = y + 0.15),
              fill = "white", color = "black", linewidth = 0.5) +
    
    # 2. Draw the node labels
    geom_text(data = nodes, 
              aes(x = x, y = y, label = name),
              size = 4.5, vjust = 0.5, hjust = 0.5) +
    
    # --- Draw residual arrows (grey, right to left) ---
    geom_segment(data = error_data,
                 aes(x = x_start, y = y, xend = x_end, yend = y),
                 color = "gray50", linewidth = 0.8,
                 arrow = arrow(type = "closed", length = unit(0.15, "inches"))) +
    
    # --- Draw residual values (to the right of the arrow tail) ---
    geom_text(data = error_data,
              aes(x = x_start + 0.05, y = y, label = label),
              size = 4, color = "gray40", hjust = 0, fontface = "italic") +
    
    # 3. Draw the main paths (with arrows)
    geom_segment(data = edges,
                 aes(x = x_start, y = y_start, xend = x_end, yend = y_end,
                     color = path_type, linewidth = linewidth),
                 arrow = arrow(type = "closed", length = unit(0.2, "inches")),
                 show.legend = FALSE) +
    
    # 4. Main-path labels
    geom_label(data = edges,
               aes(x = (x_start + x_end) / 2, y = (y_start + y_end) / 2, label = label),
               size = 3.5, fill = "white", alpha = 0.8, label.padding = unit(0.15, "lines")) +
    
    scale_color_manual(values = color_mapping) +
    scale_linewidth_continuous(range = c(0.5, 3)) +
    
    xlim(0.5, 3.3) + 
    ylim(0.5, 2.5) +
    theme_void() +
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
      plot.subtitle = element_text(hjust = 0.5, size = 10, color = "gray40"),
      plot.caption = element_text(hjust = 0.5, size = 9, color = "gray60")
    ) +
    
    labs(title = paste("Mediation Model:", title_suffix),
         subtitle = "Standardized Path Coefficients & Calc. Residuals",
         caption = "Residuals calculated from standardized betas")
  
  return(p)
}

get_friendly_name <- function(model_name) {
  case_when(
    model_name == "Total_Health" ~ "Total Health",
    model_name == "Mental_Health" ~ "Mental Health",
    model_name == "Physical_Health" ~ "Physical Health",
    model_name == "Social_Health" ~ "Social Health",
    TRUE ~ model_name
  )
}

# 3. Loop over models: plot and save (unchanged)
model_titles <- c(
  "Total_Health" = "Total Health (H_Score_Total)",
  "Mental_Health" = "Mental Health (M_Score)",
  "Physical_Health" = "Physical Health (P_Score)",
  "Social_Health" = "Social Health (S_Score)"
)

mediation_plots <- list()

for (model_name in names(model_titles)) {
  message(paste("   📊 Creating plot for:", model_name))
  p <- plot_mediation_model(model_name, model_titles[[model_name]])
  mediation_plots[[model_name]] <- p
  ggsave(paste0("Mediation_Model_", model_name, ".pdf"), p, width = 9, height = 6, dpi = 300) # a bit wider to fit the right-side arrows
}

# 4. Combined figure (unchanged)
combined_title <- "Mediation Models: Environment → Lifestyle → Health Outcomes"
combined_plot <- (mediation_plots[["Total_Health"]] + mediation_plots[["Mental_Health"]]) / 
  (mediation_plots[["Physical_Health"]] + mediation_plots[["Social_Health"]]) +
  plot_annotation(title = combined_title, 
                  subtitle = "Gray arrows indicate residual path coefficients (unexplained variance)",
                  theme = theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 16)))

ggsave("Combined_Mediation_Models.pdf", combined_plot, width = 16, height = 10, dpi = 300)

message("\nVisualisation complete. Residual arrows (e) added in the reference style.")
```



# Analysis 2: BGGM / SES controlled and uncontrolled - 0105
```{r}
# ==============================================================================
# Step 6: BGGM network analysis (sign-in-plot fix)
# ==============================================================================
library(BGGM)
library(qgraph)
library(ggplot2)
library(dplyr)
library(ggridges)
library(networktools)
library(gridExtra)

# --- 1. Basic configuration ---
out_dir <- out_fig_dir  # write to this project's Figures directory

ITER_NUM <- 5000 

e_names <- e_item_names
l_names <- l_item_names
multi_models <- list(
  "Mental_Health"   = mh_item_names, 
  "Physical_Health" = ph_item_names, 
  "Social_Health"   = sh_item_names
)

# --- Visual parameters ---
custom_node_colors <- c("Environment"="#AEC7E8", "Lifestyle"="#98DF8A", 
                        "Mental_Health"="#D8BFD8", "Physical_Health"="#FFBB78", "Social_Health"="#FFB6C1")
bridge_highlight_color <- "#FFD700" 
vsize_fixed <- 4
label_size_fixed <- 0.8  
vBorder_color <- rep("gray30", 100); vBorder_width <- rep(1, 100)

if(!exists("df_raw_bggm") || !exists("df_resid")) stop("Error: data sources not found.")

message("Configuration loaded. Fixed the loss of sign in pcor_adj.")



# ==============================================================================
# Core analysis function (force signed weights)
# ==============================================================================
run_bggm_full_metrics <- function(data_raw_full, data_resid_full, node_names, groups_list, model_label, out_dir, n_iter = ITER_NUM) {
  
  # --- 0. Data integrity check ---
  if(!all(node_names %in% colnames(data_raw_full))) {
    missing <- node_names[!node_names %in% colnames(data_raw_full)]
    stop(paste("Error: the following variables are missing from the data:", paste(missing, collapse=", ")))
  }
  
  set.seed(42)
  
  # --- 1. Prepare the data matrices ---
  Y_raw_mat <- as.matrix(data_raw_full[, node_names])
  Y_resid_mat <- as.matrix(data_resid_full[, node_names])
  mode(Y_raw_mat) <- "numeric"
  mode(Y_resid_mat) <- "numeric"
  
  # --- 2. BGGM estimation and selection ---
  fit_raw <- BGGM::estimate(Y = Y_raw_mat, iter = n_iter, progress = FALSE)
  fit_ctrl <- BGGM::estimate(Y = Y_resid_mat, iter = n_iter, progress = FALSE)
  
  sel_raw  <- BGGM::select(fit_raw,  cred = 0.99)
  sel_ctrl <- BGGM::select(fit_ctrl, cred = 0.99)
  
  # --- Robustly extract the 0/1 significance matrix ---
  get_sig_matrix <- function(bg_obj, label) {
    obj_names <- names(bg_obj)
    # Strategy 1: look for Adj_XX
    adj_candidate <- obj_names[grepl("^Adj_", obj_names)]
    if(length(adj_candidate) > 0) return(as.matrix(bg_obj[[adj_candidate[1]]]))
    # Strategy 2: look for Adj_cred
    if("Adj_cred" %in% obj_names) return(as.matrix(bg_obj$Adj_cred))
    # Strategy 3: look for pcor_adj
    if("pcor_adj" %in% obj_names) return(as.matrix(bg_obj$pcor_adj))
    
    message(paste("   ❌ [Debug] Available names in object:", paste(obj_names, collapse=", ")))
    return(NULL)
  }
  
  mat_sig_raw  <- get_sig_matrix(sel_raw, "Raw")
  mat_sig_ctrl <- get_sig_matrix(sel_ctrl, "Control")
  
  if(is.null(mat_sig_raw) || is.null(mat_sig_ctrl)) {
    stop("BGGM Error: could not locate the adjacency matrix automatically.")
  }
  
  pcor_mat_raw <- fit_raw$pcor_mat
  pcor_mat_ctrl <- fit_ctrl$pcor_mat
  
  message(paste("   🔍 [Check] Raw Pcor Range:", paste(round(range(pcor_mat_raw),3), collapse=" to ")))
  
  adj_raw  <- as.matrix(pcor_mat_raw) * as.matrix(mat_sig_raw)
  adj_ctrl <- as.matrix(pcor_mat_ctrl) * as.matrix(mat_sig_ctrl)
  
  colnames(adj_raw) <- rownames(adj_raw) <- node_names
  colnames(adj_ctrl) <- rownames(adj_ctrl) <- node_names
  
  write.csv(adj_ctrl, file.path(out_dir, paste0("adj_matrix_BGGM_", model_label, "_Pearson_Resid.csv")))
  
  # Compute correlations
  vals_raw <- adj_raw[upper.tri(adj_raw)]
  vals_ctrl <- adj_ctrl[upper.tri(adj_ctrl)]
  
  if(sd(vals_raw) == 0 || sd(vals_ctrl) == 0) {
    cor_r <- 0 
  } else {
    cor_r <- cor(vals_raw, vals_ctrl)
  }
  
  # --- 3. Prepare the community vector needed for the metrics ---
  node_count <- length(node_names)
  community_chr <- character(node_count)
  
  for (g_name in names(groups_list)) { 
    g_indices <- groups_list[[g_name]]
    valid_indices <- g_indices[g_indices <= node_count]
    if(length(valid_indices) > 0) {
      community_chr[valid_indices] <- g_name
    }
  }
  
  # --- 4. Compute bridge and node metrics ---
  br_res <- tryCatch({
    networktools::bridge(adj_ctrl, communities = community_chr, useCommunities = "all", directed = FALSE, nodes = node_names)
  }, error = function(e) {
    message("   ⚠️ Bridge metrics calculation failed: ", e$message)
    return(NULL)
  })
  
  if(!is.null(br_res)){
    val_bridge_ei <- br_res$`Bridge Expected Influence (1-step)` 
    val_bridge_str <- br_res$`Bridge Strength`                    
  } else {
    val_bridge_ei <- rep(0, node_count)
    val_bridge_str <- rep(0, node_count)
  }
  
  # Node Metrics
  val_node_ei <- colSums(adj_ctrl)       
  val_node_str <- colSums(abs(adj_ctrl)) 
  
  # --- 5. Highlight rule ---
  pos_candidates <- val_bridge_ei
  pos_candidates[pos_candidates <= 0] <- -Inf 
  
  if(all(pos_candidates == -Inf)){
    threshold <- Inf 
  } else {
    threshold <- quantile(pos_candidates[pos_candidates > -Inf], 0.8, na.rm=TRUE) 
  }
  
  top_nodes_idx <- which(val_bridge_ei >= threshold & val_bridge_ei > 0)
  
  node_colors_default <- unname(custom_node_colors[community_chr])
  node_colors_highlight <- node_colors_default
  if(length(top_nodes_idx) > 0) node_colors_highlight[top_nodes_idx] <- bridge_highlight_color
  
  # --- 6. Plotting function ---
  plot_lollipop <- function(vals, title, subtitle) {
    df <- data.frame(Node = node_names, Val = vals, Community = community_chr) %>% arrange(Val)
    df$Node <- factor(df$Node, levels = df$Node) 
    
    ggplot(df, aes(x=Node, y=Val, color=Community)) +
      geom_segment(aes(xend=Node, yend=0), color="grey") +
      geom_point(size=2.5) + coord_flip() +
      scale_color_manual(values = custom_node_colors) +
      labs(title=title, subtitle=subtitle, x="", y="Value") +
      theme_minimal() + 
      theme(legend.position="none", plot.title = element_text(size=10, face="bold"))
  }
  
  p1 <- plot_lollipop(val_bridge_ei, "Bridge Expected Influence", "Signed Sum")
  p2 <- plot_lollipop(val_bridge_str, "Bridge Strength", "Absolute Sum")
  p3 <- plot_lollipop(val_node_ei, "Node Expected Influence", "Signed Sum")
  p4 <- plot_lollipop(val_node_str, "Node Strength", "Absolute Sum")
  
  # --- 7. Return ---
  # Pre-compute the layout
  L_avg <- qgraph(adj_ctrl, layout="spring", DoNotPlot=TRUE)$layout
  
  return(list(
    adj_raw = adj_raw, adj_ctrl = adj_ctrl, cor_r = cor_r,
    p_matrix = list(p1, p2, p3, p4), 
    node_colors_default = node_colors_default,
    node_colors_highlight = node_colors_highlight,
    layout_spring = L_avg
  ))
}


# ==============================================================================
# Run the main loop
# ==============================================================================
message("\n🚀 STARTING BGGM ANALYSIS LOOP...")

pdf(file.path(out_dir, "Step6_BGGM_Results_FullMetrics.pdf"), width = 18, height = 12)

for(model_label in names(multi_models)){
  h_nodes <- multi_models[[model_label]]
  current_nodes <- c(e_names, l_names, h_nodes)
  n_e <- length(e_names); n_l <- length(l_names); n_h <- length(h_nodes)
  groups_list <- list("Environment" = 1:n_e, "Lifestyle" = (n_e+1):(n_e+n_l))
  groups_list[[model_label]] <- (n_e+n_l+1):(n_e+n_l+n_h)
  
  message(paste("\n>>> Processing:", model_label))
  
  tryCatch({
    res <- run_bggm_full_metrics(df_raw_bggm, df_resid, current_nodes, groups_list, model_label, out_dir, ITER_NUM)
    
    layout(matrix(c(1, 2), 1, 2, byrow = TRUE))

    qgraph(res$adj_raw, layout=res$layout_spring, groups=groups_list, color=res$node_colors_default,
           title=paste0(model_label, " - Raw"),
           labels=current_nodes, label.cex=label_size_fixed, vsize=vsize_fixed, border.color=vBorder_color, 
           posCol="#008000", negCol="#ff0000", 
           fade = FALSE, # force colours to show, do not fade with strength
           legend=FALSE)
    
    
    qgraph(res$adj_ctrl, layout=res$layout_spring, groups=groups_list, color=res$node_colors_default,
           title=paste0(model_label, " - Controlled\nr = "),
           labels=current_nodes, label.cex=label_size_fixed, vsize=vsize_fixed, border.color=vBorder_color, 
           posCol="#008000", negCol="#ff0000", 
           fade = FALSE, # force colours to show, do not fade with strength
           legend=FALSE)
    
    # Page 2: Highlighted Network
    layout(1)
    qgraph(res$adj_ctrl, layout=res$layout_spring, groups=groups_list, color=res$node_colors_highlight,
           title=paste(model_label, "- Final Robust Network (Highlighted)"), labels=current_nodes,
           label.cex=label_size_fixed, vsize=vsize_fixed, border.color=vBorder_color, 
           posCol="#008000", negCol="#ff0000", legend=TRUE, legend.cex=0.5)
    
    # Page 3: Metrics
    grid.arrange(res$p_matrix[[1]], res$p_matrix[[2]], res$p_matrix[[3]], res$p_matrix[[4]], ncol=2,
                 top = paste("Metrics Comparison (EI vs Strength) -", model_label))
    
    message(paste("    ✅ Completed:", model_label))
  }, error = function(e){
    message(paste("    ❌ Failed:", model_label)); message(e)
  })
}
dev.off()
message("\n🎉 Done! Polarity and weights are now correctly visualized.")
```

# Bootnet stability analysis for all models
```{r}
# ==============================================================================
# III. PHASE 3: STABILITY ANALYSIS (bootnet) - Updated for SES-Adjusted Residuals
# ==============================================================================
# Notes:
# 1. Use EBICglasso as a fast proxy for BGGM in the stability test.
# 2. Important: use df_resid (from Step 4), because SES effects have already been removed.

library(bootnet)
library(dplyr)
library(ggplot2)

message("\n🚀 STARTING PHASE 3: STABILITY ANALYSIS FOR ALL MODELS")

# 1. Basic configuration and checks
if(!exists("out_dir")) out_dir <- out_fig_dir
if(!dir.exists(out_dir)) dir.create(out_dir, recursive = TRUE)

# Key check: ensure df_resid exists
if(!exists("df_resid")) {
  stop("Error: 'df_resid' not found. Run the Step 4 code first to generate the deconfounded residual data.")
}

# Loop: Mental -> Physical -> Social
for(model_label in names(multi_models)){
  
  message(paste("\n----------------------------------------------------"))
  message(paste(">>> [Phase 3] Testing Stability for:", model_label))
  message(paste("----------------------------------------------------"))
  
  # 2. Prepare data
  nodes_extra <- multi_models[[model_label]]
  target_vars <- c(e_names, l_names, nodes_extra)
  
  data_for_boot <- df_resid %>% dplyr::select(all_of(target_vars))
  
  # 3. Define bridge communities dynamically
  n_e <- length(e_names)
  n_l <- length(l_names)
  n_h <- length(nodes_extra)
  
  communities <- list(
    "Environment" = 1:n_e,
    "Lifestyle"   = (n_e + 1):(n_e + n_l),
    "Health"      = (n_e + n_l + 1):(n_e + n_l + n_h)
  )
  
  # 4. Run bootnet
  # 4.1 Estimate the base network (EBICglasso)
  message(paste("   👉 Estimating base network (EBICglasso on Residuals)..."))
  
  network_estimate <- estimateNetwork(
    data_for_boot, 
    default = "EBICglasso", 
    corMethod = "cor", 
    tuning = 0.5,
    verbose = FALSE
  )
  
  # 4.2 Run case-dropping bootstrap
  message(paste("   👉 Running 1000 bootstraps (this takes time)..."))
  # Fix the bootnet seed
  set.seed(777)
  
  boot_res <- bootnet(
    network_estimate, 
    boots = 1000,              # 1000 recommended for a full run
    type = "case",             # case-dropping method
    statistics = c("bridgeExpectedInfluence"), # test Bridge EI only
    communities = communities, # pass the dynamic communities
    nCores = 8,                # multi-core speedup (adjust to your machine)
    verbose = FALSE
  )
  
  # 5. Compute the CS-coefficient
  # cor = 0.7 is the standard threshold (CS > 0.25 acceptable, > 0.5 excellent)
  cor_stab <- corStability(boot_res, cor = 0.7)
  cs_value <- cor_stab[1] # extract the CS value for Bridge EI
  
  message(paste("   📊 CS-coefficient (Bridge EI):", round(cs_value, 3)))
  
  # 5. Plot and save
  pdf_filename <- file.path(out_dir, paste0("Stability_CS_", model_label, ".pdf"))
  pdf(pdf_filename, width = 10, height = 6)
  
  p <- plot(boot_res, statistics = "bridgeExpectedInfluence") + 
    ggplot2::labs(title = paste("Stability of Bridge EI -", model_label),
         subtitle = paste("CS-coefficient (cor=0.7) =", round(cs_value, 3)),
         caption = "Criteria: CS > 0.25 is acceptable; CS > 0.5 is stable.") + 
    ggplot2::theme_classic() +
    ggplot2::theme(plot.title = element_text(hjust = 0.5, face="bold"),
          plot.subtitle = element_text(hjust = 0.5))
  
  print(p)
  dev.off()
  
  message(paste("   ✅ Saved plot to:", basename(pdf_filename)))
}

message("\n🎉 PHASE 3 ALL COMPLETED! Check your output folder.")
```




# Analysis 3: DAG three steps
```{r}

library(bnlearn)
library(bootnet)
library(dplyr)
library(ggplot2)

# ==============================================================================
# IV. PHASE 2: DAG ANALYSIS (Based on SES-Adjusted Residuals)
# ==============================================================================
message("\n🚀 STARTING PHASE 2: DAG ANALYSIS")

# Ensure output directories exist
if(!exists("out_dir_dag")) out_dir_dag <- file.path(out_dir, "DAG_Analysis")
if(!dir.exists(out_dir_dag)) dir.create(out_dir_dag, recursive = TRUE)

# ==============================================================================
# STEP 1: Core computation and raw-object save (computation & save raw RDS)
# ==============================================================================

message("\n🚀 [Step 1] STARTING HEAVY COMPUTATION (Bootstrap on Residuals)")
message(paste("📂 Output Directory:", out_dir_dag))

# Check that df_resid exists
if(!exists("df_resid")) stop("Error: df_resid does not exist. Run Step 4 first.")

target_models <- names(multi_models) 

for(model_label in target_models){
  
  message(paste(">>> [Computing] Running Bootstrap for:", model_label))
  
  # --- A. Data preparation (using the deconfounded residuals) ---
  nodes_extra <- multi_models[[model_label]]
  node_names_model <- c(e_names, l_names, nodes_extra)
  
  dat_resid_sub <- df_resid %>% 
    dplyr::select(all_of(node_names_model))
  
  # --- B. Blacklist setup (tiered blacklist) ---
  # Forbid: Lifestyle -> Environment
  # Forbid: Health    -> Environment
  
  non_env_nodes <- c(l_names, nodes_extra)
  
  black_list <- expand.grid(from = non_env_nodes, to = e_names, stringsAsFactors = FALSE)
  
  # --- C. Core computation (bootstrapping) ---
  tryCatch({
  # Fix the DAG bootstrap seed
    set.seed(999)
    
    start_time <- Sys.time()
    
    # Core computation: R=500 (raise to 500 or 1000 for stable results), alpha=0.01
    # Use the PC-stable algorithm
    str_fit <- boot.strength(
      data = dat_resid_sub, 
      R = 500,    # <--- recommendation: use 500 or 1000 for publication
      algorithm = "pc.stable",
      algorithm.args = list(
        blacklist = black_list, 
        alpha = 0.01  # significance level
      )
    ) 
    
    end_time <- Sys.time()
    duration <- round(difftime(end_time, start_time, units = "secs"), 1)
    message(paste("   ⏱️ Computation finished in", duration, "seconds."))
    
    # --- D. Save the raw object (.rds) ---
    rds_filename <- file.path(out_dir_dag, paste0("Boot_Object_", model_label, ".rds"))
    saveRDS(str_fit, file = rds_filename)
    
    message(paste("   💾 Saved Raw RDS:", rds_filename))
    
  }, error = function(e){
    message(paste("   ❌ Error in calculation for", model_label, ":", e$message))
  })
}

message("\n✅ [Step 1] ALL COMPUTATIONS DONE. Raw data saved to .rds files.")
message("👉 Next: Run 'Step 2' (Sensitivity) and 'Step 3' (Plotting).")

```



```{r}
library(bnlearn)
library(dplyr)
library(ggplot2) # ggplot2 is used for the line plot

library(bnlearn)
library(dplyr)
library(ggplot2) 

# ==============================================================================
# STEP 2: Sensitivity analysis (with CSV export and elbow plot) - extended
# ==============================================================================

message("\n📊 [Step 2] STARTING SENSITIVITY CHECK & PLOTTING")

# Define the test range
test_thresholds <- sort(unique(c(seq(0.70, 0.95, by = 0.05), 0.98)))

# Define the thresholds for which a CSV should be exported
export_targets <- c(0.70, 0.75, 0.80, 0.85, 0.90, 0.95)

target_models <- names(multi_models)

for(model_label in target_models){
  
  # --- 1. Read the RDS file saved in Step 1 ---
  rds_file <- file.path(out_dir_dag, paste0("Boot_Object_", model_label, ".rds"))
  
  if(!file.exists(rds_file)){
    message(paste("⚠️ Skipped:", model_label, "(RDS file not found)"))
    next
  }
  
  message(paste("\n>>> Analyzing Model:", model_label))
  str_fit <- readRDS(rds_file)
  
  # --- 2. Loop over thresholds and count edges ---
  results_list <- list()
  
  for(th in test_thresholds){
    # Compute the averaged network
    avg <- averaged.network(str_fit, threshold = th)
    # Count the edges
    final_arcs <- as.data.frame(avg$arcs)
    num_edges <- nrow(final_arcs)
    
    # ---------------------------------------------------------
    # If this is a target threshold (85, 90, 95), save a CSV immediately
    # ---------------------------------------------------------
    if(th %in% export_targets){
      # example filename: DAG_Arrows_0.9_Mental_Health.csv
      arrow_file <- file.path(out_dir_dag, paste0("DAG_Arrows_", th, "_", model_label, ".csv"))
      
      if(num_edges > 0){
        write.csv(final_arcs, arrow_file, row.names = FALSE)
        message(paste0("      💾 [Export] Saved arrows for threshold ", th, " (Edges: ", num_edges, ")"))
      } else {
        message(paste0("      ⚠️ [Export] Threshold ", th, " has 0 edges, skip saving."))
      }
    }
    # ---------------------------------------------------------
    
    # Auto-generate a description (for reference only)
    desc <- ""
    if(num_edges > 100) desc <- "Very Dense"
    else if(num_edges > 50) desc <- "Dense"
    else if(num_edges >= 20) desc <- "Moderate (Interpretable)"
    else if(num_edges > 5) desc <- "Sparse (Skeleton)"
    else desc <- "Very Sparse"
    
    # Store in the list
    results_list[[as.character(th)]] <- data.frame(
      Threshold = th,
      Edge_Count = num_edges,
      Description = desc,
      stringsAsFactors = FALSE
    )
  }
  
  # Combine into a data frame
  df_results <- do.call(rbind, results_list)
  
  # --- 3. Export the summary CSV (for the supplement) ---
  csv_name <- file.path(out_dir_dag, paste0("Sensitivity_Table_", model_label, ".csv"))
  write.csv(df_results, csv_name, row.names = FALSE)
  message(paste("   💾 Summary Table Saved:", csv_name))
  
  # --- 4. Draw the line plot (scree plot) ---
  p <- ggplot(df_results, aes(x = Threshold, y = Edge_Count)) +
    geom_line(color = "steelblue", size = 1.2) +
    geom_point(color = "steelblue", size = 3) +
    geom_text(aes(label = Edge_Count), vjust = -0.8, size = 3.5) +
    # Mark the 0.85 and 0.90 positions
    geom_vline(xintercept = c(0.85, 0.90, 0.95), linetype = "dashed", color = "gray50") +
    scale_x_continuous(breaks = test_thresholds) +
    theme_minimal() +
    labs(
      title = paste("Sensitivity Analysis:", model_label),
      subtitle = "Number of Edges vs. Inclusion Threshold",
      x = "Threshold (Bootstrap Confidence)",
      y = "Number of Edges (Complexity)"
    ) +
    theme(
      plot.title = element_text(face = "bold", size = 14),
      axis.text = element_text(size = 11)
    )
  
  plot_name <- file.path(out_dir_dag, paste0("Sensitivity_Plot_", model_label, ".pdf"))
  ggsave(plot_name, plot = p, width = 8, height = 6)
  message(paste("   📈 Plot Saved:", plot_name))
}

message("\n✅ [Step 2] Analysis Done.")
message("👉 Checked Output folder for new 'DAG_Arrows_0.XX_....csv' files.")
```


# DAG_Layered plot
library(qgraph)
library(dplyr)
library(bnlearn)

# ==============================================================================
# STEP 3: Final plotting (debug-fixed - resolves node-name mismatch)
# ==============================================================================

FINAL_THRESHOLD <- 0.70

message(paste("\n🎨 [Step 3 Debug] STARTING PLOTTING | Threshold:", FINAL_THRESHOLD))

target_models <- names(multi_models) 

for(model_label in target_models){
  
  # --- 1. Read the raw data ---
  rds_file <- file.path(out_dir_dag, paste0("Boot_Object_", model_label, ".rds"))
  
  if(!file.exists(rds_file)){
    message(paste("⚠️ Skipped:", model_label, "(RDS not found)"))
    next
  }
  
  str_fit <- readRDS(rds_file)
  
  # --- 2. Filter edges ---
  avg_dag <- averaged.network(str_fit, threshold = FINAL_THRESHOLD)
  final_arcs <- as.data.frame(avg_dag$arcs)
  
  all_nodes <- nodes(avg_dag) 
  n_total <- length(all_nodes)
  
  # --- Diagnostic report ---
  message(paste0("\n>>> [Diagnostic] Model: ", model_label))
  message(paste0("    1. Theoretical Edges (from Table): ", nrow(final_arcs)))
  message(paste0("    2. Total Nodes found: ", n_total))
  if(nrow(final_arcs) > 0){
    message(paste0("    3. First edge sample: ", final_arcs[1,1], " -> ", final_arcs[1,2]))
    message(paste0("    4. First node name:   ", all_nodes[1]))
  }
  
  # --- 3. Prepare the plotting matrices ---
  # A. Adjacency matrix
  dag_adj <- matrix(0, nrow = n_total, ncol = n_total)
  rownames(dag_adj) <- colnames(dag_adj) <- all_nodes
  
  # B. Edge-colour matrix
  edge_col_mat <- matrix("black", nrow = n_total, ncol = n_total)
  rownames(edge_col_mat) <- colnames(edge_col_mat) <- all_nodes 
  
  get_group_id_safe <- function(node_name_clean){
    
    
    
    e_names_safe <- make.names(e_names)
    l_names_safe <- make.names(l_names)
    
    if(node_name_clean %in% e_names || node_name_clean %in% e_names_safe) return(1)
    if(node_name_clean %in% l_names || node_name_clean %in% l_names_safe) return(2)
    return(3) # everything else is Health
  }
  
  # --- 4. Fill the matrices ---
  matches_count <- 0
  if(nrow(final_arcs) > 0){
    for(i in 1:nrow(final_arcs)){
      f <- final_arcs[i, "from"]
      t <- final_arcs[i, "to"]
      
      if(f %in% all_nodes && t %in% all_nodes){
        dag_adj[f, t] <- 1
        matches_count <- matches_count + 1
        
        g_src <- get_group_id_safe(f)
        g_dst <- get_group_id_safe(t)
        
        if(g_src == g_dst) edge_col_mat[f, t] <- "gray80"      
        else if(g_src < g_dst) edge_col_mat[f, t] <- "forestgreen" 
        else edge_col_mat[f, t] <- "firebrick2"  
      }
    }
  }
  message(paste0("    5. Edges successfully plotted: ", matches_count, " / ", nrow(final_arcs)))

  # --- 5. Build the layered layout (adapted to the new names) ---
  Layout_Matrix <- matrix(0, nrow = n_total, ncol = 2)
  
  group_ids <- sapply(all_nodes, get_group_id_safe)
  
  idx_e <- which(group_ids == 1)
  idx_l <- which(group_ids == 2)
  idx_h <- which(group_ids == 3)
  
  # E (Top)
  if(length(idx_e) > 0){
    Layout_Matrix[idx_e, 1] <- seq(-2.4, 2.4, length.out = length(idx_e))
    Layout_Matrix[idx_e, 2] <- 1.0
  }
  # L (Mid)
  if(length(idx_l) > 0){
    Layout_Matrix[idx_l, 1] <- seq(-1.6, 1.6, length.out = length(idx_l))
    Layout_Matrix[idx_l, 2] <- 0.0
  }
  # H (Bot)
  if(length(idx_h) > 0){
    Layout_Matrix[idx_h, 1] <- seq(-0.8, 0.8, length.out = length(idx_h))
    Layout_Matrix[idx_h, 2] <- -1.0
  }

  # --- 5. Plot ---
  # Community list
  groups_model <- list("Environment" = 1:n_e, "Lifestyle" = (n_e + 1):(n_e + n_l))
  groups_model[[model_label]] <- (n_e + n_l + 1):(n_e + n_l + n_h)
  current_colors <- custom_node_colors[names(groups_model)]

  tryCatch({
    pdf(file.path(out_dir_dag, paste0("DAG_Layered_", model_label, ".pdf")), width = 32, height = 16)
    
    qgraph(dag_adj, 
           layout = Layout_Matrix, # not "spring"; pass the coordinate matrix directly
           
           rescale = TRUE,         # auto-rescale to fit the canvas
           
           # === Style ===
           edge.color = edge_col_mat, 
           groups = groups_model,           
           color = current_colors, 
           labels = colnames(dag_adj), 
           vsize = 2.5,
           label.cex = 0.8,
           border.color = "gray30",
           
           nodeNames = NULL,
           legend = TRUE, 
           legend.cex = 0.5,
           
           directed = TRUE,
           mode = "direct",
           esize = 1.2,
           asize = 2.0,
           
           curve = 0.3,     # 0 = straight; larger = more curved
           curveAll = TRUE, # curve all edges to avoid passing through middle nodes
           
           title = paste("DAG Structure (Layered):", model_label),
           title.cex = 1.6,
           mar = c(9, 5, 5, 3)
    )
    
    mtext(param_label_1, side = 1, line = 3, adj = 0, cex = 0.85, col = "gray40", font = 3)
    mtext(param_label_2, side = 1, line = 4.5, adj = 0, cex = 0.85, col = "gray40", font = 3)
    
    dev.off()
    message(paste("   ✅ Layered Plot Saved:", model_label))
    
  }, error = function(e){
    message(paste("   ❌ Error:", e$message))
    if(dev.cur() > 1) dev.off()
  })

}


# layered DAG plot with layered layout

library(qgraph)
library(dplyr)
library(bnlearn)

# ==============================================================================
# STEP 3: Final plotting (vertical spacing x3)
# ==============================================================================

FINAL_THRESHOLD <- 0.70 # or 0.90, your choice

# Define the parameter labels
param_label_1 <- paste0("Threshold: ", FINAL_THRESHOLD, " | Bootstrap: 100")
param_label_2 <- "Green: Forward | Red: Feedback | Gray: Within-Group"

message(paste("\n🎨 [Step 3] STARTING PLOTTING | Threshold:", FINAL_THRESHOLD))

target_models <- names(multi_models) 

for(model_label in target_models){
  
  # --- 1. Read the raw data (keep the RDS read) ---
  rds_file <- file.path(out_dir_dag, paste0("Boot_Object_", model_label, ".rds"))
  
  if(!file.exists(rds_file)){
    message(paste("⚠️ Skipped:", model_label, "(RDS not found)"))
    next
  }
  
  str_fit <- readRDS(rds_file)
  
  # --- 2. Filter edges ---
  avg_dag <- averaged.network(str_fit, threshold = FINAL_THRESHOLD)
  final_arcs <- as.data.frame(avg_dag$arcs)
  
  all_nodes <- nodes(avg_dag) 
  n_total <- length(all_nodes)
  
  # --- 3. Prepare the plotting matrices ---
  # A. Adjacency matrix
  dag_adj <- matrix(0, nrow = n_total, ncol = n_total)
  rownames(dag_adj) <- colnames(dag_adj) <- all_nodes
  
  # B. Edge-colour matrix
  edge_col_mat <- matrix("black", nrow = n_total, ncol = n_total)
  rownames(edge_col_mat) <- colnames(edge_col_mat) <- all_nodes 
  
  # C. Safe group assignment
  get_group_id_safe <- function(node_name_clean){
    e_names_safe <- make.names(e_names)
    l_names_safe <- make.names(l_names)
    if(node_name_clean %in% e_names || node_name_clean %in% e_names_safe) return(1)
    if(node_name_clean %in% l_names || node_name_clean %in% l_names_safe) return(2)
    return(3) 
  }
  
  # --- 4. Fill the matrices ---
  if(nrow(final_arcs) > 0){
    for(i in 1:nrow(final_arcs)){
      f <- final_arcs[i, "from"]
      t <- final_arcs[i, "to"]
      
      if(f %in% all_nodes && t %in% all_nodes){
        dag_adj[f, t] <- 1
        
        g_src <- get_group_id_safe(f)
        g_dst <- get_group_id_safe(t)
        
        if(g_src == g_dst) edge_col_mat[f, t] <- "gray80"       
        else if(g_src < g_dst) edge_col_mat[f, t] <- "forestgreen" 
        else edge_col_mat[f, t] <- "firebrick2"  
      }
    }
  }

  # --- 5. Build the layered layout (increased vertical spacing) ---
  Layout_Matrix <- matrix(0, nrow = n_total, ncol = 2)
  
  # Get the actual indices
  group_ids <- sapply(all_nodes, get_group_id_safe)
  idx_e <- which(group_ids == 1)
  idx_l <- which(group_ids == 2)
  idx_h <- which(group_ids == 3)
  
  
  # E (top): Y changed from 1.0 to 3.0
  if(length(idx_e) > 0){
    Layout_Matrix[idx_e, 1] <- seq(-2.4, 2.4, length.out = length(idx_e))
    Layout_Matrix[idx_e, 2] <- 3.0 
  }
  # L (mid): Y stays 0.0
  if(length(idx_l) > 0){
    Layout_Matrix[idx_l, 1] <- seq(-1.6, 1.6, length.out = length(idx_l))
    Layout_Matrix[idx_l, 2] <- 0.0
  }
  # H (bottom): Y changed from -1.0 to -3.0
  if(length(idx_h) > 0){
    Layout_Matrix[idx_h, 1] <- seq(-0.8, 0.8, length.out = length(idx_h))
    Layout_Matrix[idx_h, 2] <- -3.0
  }

  # --- 6. Define communities ---
  groups_list <- list(
    "Environment" = idx_e,
    "Lifestyle"   = idx_l
  )
  groups_list[[model_label]] <- idx_h 
  
  # Colour matching
  my_colors <- c(
    if("Environment" %in% names(custom_node_colors)) custom_node_colors["Environment"] else "#A6CEE3",
    if("Lifestyle" %in% names(custom_node_colors)) custom_node_colors["Lifestyle"] else "#B2DF8A",
    if(model_label %in% names(custom_node_colors)) custom_node_colors[model_label] else "#FB9A99"
  )

  # --- 7. Plot (keeping your parameters exactly) ---
  tryCatch({
    pdf_name <- file.path(out_dir_dag, paste0("DAG_Layered2_", model_label, ".pdf"))
    pdf(pdf_name, width = 32, height = 16)
    
    qgraph(dag_adj, 
           layout = Layout_Matrix, 
           rescale = TRUE,
           
           # === Style ===
           edge.color = edge_col_mat, 
           groups = groups_list,
           color = my_colors, 
           labels = colnames(dag_adj), 
           
           vsize = 2.5,
           label.cex = 0.8,
           
           border.color = "gray30",
           nodeNames = NULL,
           legend = TRUE, 
           legend.cex = 0.5, 
           
           directed = TRUE,
           mode = "direct",
           esize = 1.2,
           asize = 2.0,
           
           curve = 0.3,     
           curveAll = TRUE,
           
           title = paste("DAG Structure (Layered):", model_label),
           title.cex = 1.6,
           mar = c(9, 5, 5, 3) 
    )
    
    mtext(param_label_1, side = 1, line = 3, adj = 0, cex = 0.85, col = "gray40", font = 3)
    mtext(param_label_2, side = 1, line = 4.5, adj = 0, cex = 0.85, col = "gray40", font = 3)
    
    dev.off()
    message(paste("   ✅ Layered Plot Saved (Vertical Spacing x3):", model_label))
    
  }, error = function(e){
    message(paste("   ❌ Error:", e$message))
    if(dev.cur() > 1) dev.off()
  })
}


# DAG_Spring_plot
```{r}
library(qgraph)
library(dplyr)
library(bnlearn)


# STEP 3: Final plotting (free layout + high-repulsion comparison)


FINAL_THRESHOLD <- 0.70 # or 0.90

# Labels
param_label_1 <- paste0("Threshold: ", FINAL_THRESHOLD, " | Layout: High Repulsion Spring")
param_label_2 <- "Green: Forward | Red: Feedback | Gray: Within-Group"

message(paste("\n🎨 [Step 3 Contrast] STARTING FORCE-DIRECTED PLOTTING | Threshold:", FINAL_THRESHOLD))

target_models <- names(multi_models) 

for(model_label in target_models){
  
  # --- 1. Read the raw data (unchanged) ---
  rds_file <- file.path(out_dir_dag, paste0("Boot_Object_", model_label, ".rds"))
  
  if(!file.exists(rds_file)){
    message(paste("⚠️ Skipped:", model_label, "(RDS not found)"))
    next
  }
  
  str_fit <- readRDS(rds_file)
  
  # --- 2. Filter edges ---
  avg_dag <- averaged.network(str_fit, threshold = FINAL_THRESHOLD)
  final_arcs <- as.data.frame(avg_dag$arcs)
  all_nodes <- nodes(avg_dag) 
  n_total <- length(all_nodes)
  
  # --- 3. Prepare matrices ---
  dag_adj <- matrix(0, nrow = n_total, ncol = n_total)
  rownames(dag_adj) <- colnames(dag_adj) <- all_nodes
  
  edge_col_mat <- matrix("black", nrow = n_total, ncol = n_total)
  rownames(edge_col_mat) <- colnames(edge_col_mat) <- all_nodes 
  
  # Group-assignment helper function
  get_group_id_safe <- function(node_name_clean){
    e_names_safe <- make.names(e_names)
    l_names_safe <- make.names(l_names)
    if(node_name_clean %in% e_names || node_name_clean %in% e_names_safe) return(1)
    if(node_name_clean %in% l_names || node_name_clean %in% l_names_safe) return(2)
    return(3) 
  }
  
  # --- 4. Fill matrices & colour edges ---
  if(nrow(final_arcs) > 0){
    for(i in 1:nrow(final_arcs)){
      f <- final_arcs[i, "from"]
      t <- final_arcs[i, "to"]
      
      if(f %in% all_nodes && t %in% all_nodes){
        dag_adj[f, t] <- 1
        
        g_src <- get_group_id_safe(f)
        g_dst <- get_group_id_safe(t)
        
        if(g_src == g_dst) edge_col_mat[f, t] <- "gray80"       
        else if(g_src < g_dst) edge_col_mat[f, t] <- "forestgreen" 
        else edge_col_mat[f, t] <- "firebrick2"  
      }
    }
  }

  # --- 5. Define communities (keep the index logic) ---
  group_ids <- sapply(all_nodes, get_group_id_safe)
  idx_e <- which(group_ids == 1)
  idx_l <- which(group_ids == 2)
  idx_h <- which(group_ids == 3)
  
  groups_list <- list("Environment" = idx_e, "Lifestyle" = idx_l)
  groups_list[[model_label]] <- idx_h 
  
  my_colors <- c(
    if("Environment" %in% names(custom_node_colors)) custom_node_colors["Environment"] else "#A6CEE3",
    if("Lifestyle" %in% names(custom_node_colors)) custom_node_colors["Lifestyle"] else "#B2DF8A",
    if(model_label %in% names(custom_node_colors)) custom_node_colors[model_label] else "#FB9A99"
  )

  # --- 6. Plot (free layout) ---
  tryCatch({
    pdf_name <- file.path(out_dir_dag, paste0("DAG_Spring_", model_label, ".pdf"))
    
    pdf(pdf_name, width = 32, height = 16)
    
    qgraph(dag_adj, 
           layout = "spring",
           layout.par = list(
             repulsion = 3.0,      # repulsion: very strong (default ~1), pushes nodes far apart
             area = n_total^3.5,   # area: large, lets nodes spread out fully
             cool.exp = 1.1,       # cooling exponent
             niter = 5000          # iterations: run longer for a more stable structure
           ),
           
           rescale = TRUE,
           
           # === Style (unchanged) ===
           edge.color = edge_col_mat, 
           groups = groups_list,
           color = my_colors, 
           labels = colnames(dag_adj), 
           
           vsize = 2.5,
           label.cex = 0.8,
           
           border.color = "gray30",
           nodeNames = NULL,
           legend = TRUE, 
           legend.cex = 0.5,
           
           directed = TRUE,
           mode = "direct",
           esize = 1.2,
           asize = 2.0,
           
           curve = 0.3,     
           curveAll = TRUE, 
           
           title = paste("DAG Structure (Free Spring Layout):", model_label),
           title.cex = 1.6,
           mar = c(9, 5, 5, 3)
    )
    
    mtext(param_label_1, side = 1, line = 3, adj = 0, cex = 0.85, col = "gray40", font = 3)
    mtext(param_label_2, side = 1, line = 4.5, adj = 0, cex = 0.85, col = "gray40", font = 3)
    
    dev.off()
    message(paste("   ✅ Spring Layout Plot Saved:", model_label))
    
  }, error = function(e){
    message(paste("   ❌ Error:", e$message))
    if(dev.cur() > 1) dev.off()
  })
}
```


# Summary: BGGM and DAG integration visulization
```{r}
# ==============================================================================
# 0. Setup & global configuration
# ==============================================================================
library(ggplot2)
library(dplyr)
library(tidyr)
library(networktools) 
library(tibble)
library(ggalluvial)
library(bnlearn) # required for handling the RDS objects

# Path configuration
out_dir     <- out_fig_dir
# Important: make sure your .rds files (Boot_Object_...) are under out_fig_dir/DAG_Analysis
out_dir_dag <- file.path(out_fig_dir, "DAG_Analysis")

if(!dir.exists(out_dir)) dir.create(out_dir, recursive=TRUE)

# Key: set the DAG threshold (must match the Step 3 plotting exactly)
DAG_THRESHOLD <- 0.70  

models <- c("Mental_Health", "Physical_Health", "Social_Health")

# --- Colour scheme ---
my_colors <- c(
  "Environment"     = "#AEC7E8",  
  "Lifestyle"       = "#98DF8A",  
  "Mental_Health"   = "#D8BFD8",  
  "Physical_Health" = "#FFBB78",  
  "Social_Health"   = "#FFB6C1"   
)


heatmap_neg <- "#CD5C5C" 
heatmap_mid <- "white"   
heatmap_pos <- "#2E8B57"


# ==============================================================================
# 🎯 Figure 3 Combined: Shared Y-Axis + Dual Bridge Asterisks
# ==============================================================================
library(ggplot2)
library(dplyr)
library(tidyr)
library(networktools)
library(tibble)
library(bnlearn)
library(patchwork)
library(scales) 


# Asterisk colours
color_env_bridge <- "#800080" # purple (Environment)
color_health_bridge <- "#0000FF" # blue (Health)

message("\n========== Generating Figure 3 (dual asterisks) ==========")

# --- Step 1: Gather all data and compute bridge centrality ---
list_edges <- list()
all_y_nodes <- c() 

for (model_label in models) {

# A. Read BGGM (auto-detect separator)
  # --------------------------------------------------------
  bggm_file <- file.path(out_dir, paste0("adj_matrix_BGGM_", model_label, "_Pearson_Resid.csv"))
  
  if (!file.exists(bggm_file)) {
    message(paste0("Resid file not found, trying the NPN file..."))
    bggm_file <- file.path(out_dir, paste0("adj_matrix_BGGM_", model_label, "_Pearson_Resid.csv"))
  }
  
  if (!file.exists(bggm_file)) next

  first_line <- readLines(bggm_file, n = 1)
  
  raw_data <- read.csv(bggm_file, check.names = FALSE)
  
  if (ncol(raw_data) <= 1) {
    message(paste0("   CSV format looks wrong (<=1 column), trying semicolon (;)..."))
    raw_data <- read.csv(bggm_file, sep = ";", check.names = FALSE)
  }
  
  if (ncol(raw_data) <= 1) {
    message(paste0("   still unresolved, trying tab (\t)..."))
    raw_data <- read.table(bggm_file, sep = "\t", header = TRUE, check.names = FALSE)
  }

  # 5. Handle row names
  if (ncol(raw_data) > 1) {
    rownames(raw_data) <- raw_data[, 1]
    adj_mat <- as.matrix(raw_data[, -1])
  } else {
    message("   Serious error: could not parse data columns; check the CSV separator manually.")
    message(paste0("   first line of the file: ", first_line))
    next
  }

  
  # B. Bridge EI computation
  node_names <- colnames(adj_mat)
  communities_vec <- case_when(grepl("^E", node_names) ~ "Environment", grepl("^L", node_names) ~ "Lifestyle", TRUE ~ "Health")
  
  bridge_map <- tryCatch({
    bridge_res <- networktools::bridge(adj_mat, communities = communities_vec, useCommunities = "all", directed = FALSE)
    df_bridge <- data.frame(Node = node_names, Bridge_EI = bridge_res$`Bridge Expected Influence (1-step)`)
    
    # Keep the top 20%
    threshold <- quantile(df_bridge$Bridge_EI, 0.80, na.rm = TRUE) 
    setNames((df_bridge$Bridge_EI >= threshold) & (df_bridge$Bridge_EI > 0), df_bridge$Node)
    
  }, error = function(e) setNames(rep(FALSE, length(node_names)), node_names))
  
  # C. Read the DAG
  rds_file <- file.path(out_dir_dag, paste0("Boot_Object_", model_label, ".rds"))
  dag_keys <- character()
  dag_status <- "not found / failed to load"
  
  if (file.exists(rds_file)) {
    str_fit <- readRDS(rds_file)
    avg_dag <- averaged.network(str_fit, threshold = DAG_THRESHOLD)
    dag_arcs <- as.data.frame(avg_dag$arcs)
    if(nrow(dag_arcs) > 0) {
        # Build safe keys
        dag_keys <- paste0(make.names(dag_arcs$from), "->", make.names(dag_arcs$to))
        dag_status <- paste0("loaded (edges: ", nrow(dag_arcs), ")")
    } else {
        dag_status <- "loaded but no edges (threshold too high?)"
    }
  }

  # ============================================================
  # Data integrity check (diagnostic)
  # ============================================================
  message(paste0("\n--------------------------------------------------"))
  message(paste0("Checking model: [", model_label, "]"))
  message(paste0("   1. BGGM matrix: ", nrow(adj_mat), " rows x ", ncol(adj_mat), " cols"))
  message(paste0("   2. sample variable names: ", paste(head(node_names, 3), collapse=", ")))
  message(paste0("   3. DAG status: ", dag_status))
  
  if(length(dag_keys) > 0) {
      message(paste0("   4. sample DAG keys (make.names):"))
      message(paste0("      -> ", head(dag_keys, 2)))
  }
  message(paste0("--------------------------------------------------\n"))
  # ============================================================

  
# D. Build the data (robust version: direct matrix indexing)
# -----------------------------------------------------------
# 1. Ensure it is a matrix
  adj_mat <- as.matrix(adj_mat)
  
  indices <- which(adj_mat != 0, arr.ind = TRUE)
  
  if (nrow(indices) > 0) {
    edges_df <- data.frame(
      V1_str = rownames(adj_mat)[indices[, 1]],
      V2_str = colnames(adj_mat)[indices[, 2]],
      Freq   = adj_mat[indices],
      stringsAsFactors = FALSE
    )
  } else {
    edges_df <- data.frame(V1_str=character(), V2_str=character(), Freq=numeric())
  }

  edges_df <- edges_df %>% 
    mutate(
      Type_From = case_when(grepl("^E", .data$V1_str) ~ "E", grepl("^L", .data$V1_str) ~ "L", TRUE ~ "H"),
      Type_To   = case_when(grepl("^E", .data$V2_str) ~ "E", grepl("^L", .data$V2_str) ~ "L", TRUE ~ "H")
    ) %>%
    # keep cross-level edges only
    filter((Type_From == "E" & Type_To == "H") | (Type_From == "H" & Type_To == "E")) %>%
    mutate(
      Source = ifelse(Type_From == "E", V1_str, V2_str),
      Target = ifelse(Type_To == "H", V2_str, V1_str),
      
      Is_Env_Bridge = bridge_map[Source],
      Is_Health_Bridge = bridge_map[Target],

      Expected_Key = paste0(make.names(Source), "->", make.names(Target)),
      Reverse_Key  = paste0(make.names(Target), "->", make.names(Source)),
  
      Direction_Type = case_when(
        Expected_Key %in% dag_keys ~ "Expected (E->H)", 
        Reverse_Key %in% dag_keys ~ "Reverse (H->E)", 
        TRUE ~ NA_character_
      )
    )
  
  if (nrow(edges_df) > 0) {
    list_edges[[model_label]] <- edges_df
    all_y_nodes <- c(all_y_nodes, unique(edges_df$Source)) 
  }
}

unified_y_levels <- sort(unique(all_y_nodes))

# --- Step 2: Plot ---
plot_list <- list()

for (i in seq_along(models)) {
  model_label <- models[i]
  if(is.null(list_edges[[model_label]])) next
  df_curr <- list_edges[[model_label]]
  clean_title <- gsub("_", " ", model_label)
  show_y_axis <- (i == 1)
  
  p <- ggplot(df_curr, aes(x = Target, y = Source)) + 
    coord_fixed(ratio = 1) +
    
    # 1. Heatmap
    geom_tile(aes(fill = Freq), color = "white", linewidth = 0.5) + 
    scale_fill_gradient2(low = heatmap_neg, mid = heatmap_mid, high = heatmap_pos, 
                         midpoint = 0, limits = c(-0.1, 0.1), oob = scales::squish, name = "Partial Correlation") +
    
    # 2. Values (nudged down)
    geom_text(aes(label = sprintf("%.2f", Freq)), size = 2.8, color = "black", fontface = "bold", position = position_nudge(y = -0.15)) +
    
    # 3. Environment-factor asterisk (top-left, purple)
    geom_text(data = subset(df_curr, Is_Env_Bridge), 
              label = "*", color = color_env_bridge, size = 6, fontface = "bold",
              position = position_nudge(x = -0.3, y = 0.25)) +
    
    # 4. Health-factor asterisk (top-right, blue)
    geom_text(data = subset(df_curr, Is_Health_Bridge), 
              label = "*", color = color_health_bridge, size = 6, fontface = "bold",
              position = position_nudge(x = 0.3, y = 0.25)) +
    
    # 5. Direction marker (upper-centre)
    geom_point(aes(shape = Direction_Type), color = "black", size = 3, na.rm = TRUE, position = position_nudge(y = 0.15)) +
    geom_point(aes(shape = Direction_Type, color = Direction_Type), size = 2, na.rm = TRUE, position = position_nudge(y = 0.15)) +
    
    scale_shape_manual(values = c("Expected (E->H)" = 19, "Reverse (H->E)" = 17)) +
    scale_color_manual(values = c("Expected (E->H)" = "#FFD700", "Reverse (H->E)" = "#CD5C5C")) +
    scale_y_discrete(limits = unified_y_levels, drop = FALSE) +
    
    theme_minimal() +
    theme(
      panel.grid = element_blank(),
      axis.text.x = element_text(angle = 45, hjust = 1, size = 9, color = "black"),
      axis.text.y = if(show_y_axis) element_text(size = 9, color = "black") else element_blank(),
      axis.title.y = if(show_y_axis) element_text(size = 10, face="bold") else element_blank(),
      axis.ticks.y = if(show_y_axis) element_line() else element_blank(),
      plot.title = element_text(face = "bold", size = 12, hjust = 0.5),
      panel.border = element_rect(color = "grey80", fill = NA, linewidth = 0.5),
      legend.position = "bottom",
      legend.box = "horizontal"
    ) +
    labs(title = clean_title, x = NULL, y = if(show_y_axis) "Environmental Factors" else NULL)
  
  plot_list[[model_label]] <- p
}

# --- Step 3: Assemble the panels ---
if (length(plot_list) > 0) {
  
  combined_plot <- wrap_plots(plot_list, ncol = 3) + 
    plot_layout(guides = "collect") + 
    plot_annotation(
      title = "Figure 3: Direct Pathways across Health Domains (Dual Bridge Markers)",
      subtitle = paste0("Note: Top-Left Purple '*' = Environment Bridge; Top-Right Blue '*' = Health Bridge.\n", "Color range [-0.1, 0.1]. Shapes indicate DAG direction."),
      theme = theme(
        plot.title = element_text(size = 16, face = "bold"),
        plot.subtitle = element_text(size = 11, color = "gray30")
      )
    )
  
  ggsave(file.path(out_dir, "Figure3_Combined_DualStars.pdf"), combined_plot, width = 18, height = 7)
  print(combined_plot)
  message("Figure 3 (dual stars) complete.")
  
} else {
  message("No data.")
}

# ==============================================================================
# Refined Figure 3: bubble matrix - red/green colour version
# ==============================================================================
library(ggplot2)
library(patchwork)
library(scales)
library(here)
library(networktools)

message("\n========== Generating the red/green bubble matrix ==========")

# --- 1. Paths and configuration ---
source_dir <- here::here("output")
save_dir   <- here::here("plot")
if(!dir.exists(save_dir)) dir.create(save_dir, recursive = TRUE)

models <- c("Mental_Health", "Physical_Health", "Social_Health")
color_env_bridge <- "#800080" 
color_health_bridge <- "#0000FF"

color_pos <- "#228B22"  # forest green (positive)
color_neg <- "#EE2C2C"  # firebrick red (negative)
color_mid <- "#F7F7F7"  # very light grey

plot_list <- list()

# --- 2. Loop ---
for (i in seq_along(models)) {
  model_label <- models[i]
  
  # A. Read data (brief)
  bggm_file <- file.path(source_dir, paste0("adj_matrix_BGGM_", model_label, "_Pearson_Resid.csv"))
  if (!file.exists(bggm_file)) bggm_file <- here::here("plot", paste0("adj_matrix_BGGM_", model_label, "_Pearson_Resid.csv"))
  if (!file.exists(bggm_file)) next
  raw_data <- read.csv(bggm_file, check.names = FALSE)
  if (ncol(raw_data) <= 1) raw_data <- read.csv(bggm_file, sep = ";", check.names = FALSE)
  if (ncol(raw_data) > 1) { rownames(raw_data) <- raw_data[, 1]; adj_mat <- as.matrix(raw_data[, -1]) } else next

  # B. Compute bridge centrality
  node_names <- colnames(adj_mat)
  communities_vec <- case_when(grepl("^E", node_names) ~ "Environment", grepl("^L", node_names) ~ "Lifestyle", TRUE ~ "Health")
  bridge_map <- tryCatch({
    bridge_res <- networktools::bridge(adj_mat, communities = communities_vec, useCommunities = "all", directed = FALSE)
    df_bridge <- data.frame(Node = node_names, Bridge_EI = bridge_res$`Bridge Expected Influence (1-step)`)
    threshold <- quantile(df_bridge$Bridge_EI, 0.80, na.rm = TRUE) 
    setNames((df_bridge$Bridge_EI >= threshold) & (df_bridge$Bridge_EI > 0), df_bridge$Node)
  }, error = function(e) setNames(rep(FALSE, length(node_names)), node_names))

  # C. Extract edge data
  indices <- which(adj_mat != 0, arr.ind = TRUE)
  if(nrow(indices) == 0) next
  df_curr <- data.frame(Source = rownames(adj_mat)[indices[, 1]], Target = colnames(adj_mat)[indices[, 2]], Freq = adj_mat[indices], stringsAsFactors = FALSE) %>%
    mutate(Type_From = case_when(grepl("^E", Source) ~ "E", grepl("^L", Source) ~ "L", TRUE ~ "H"),
           Type_To   = case_when(grepl("^E", Target) ~ "E", grepl("^L", Target) ~ "L", TRUE ~ "H")) %>%
    filter((Type_From == "E" & Type_To == "H") | (Type_From == "H" & Type_To == "E")) %>%
    mutate(Real_Source = ifelse(Type_From == "E", Source, Target), Real_Target = ifelse(Type_To == "H", Target, Source),
           Is_Env_Bridge = bridge_map[Real_Source], Is_Health_Bridge = bridge_map[Real_Target]) %>%
    select(Source = Real_Source, Target = Real_Target, Freq, Is_Env_Bridge, Is_Health_Bridge)

  if(nrow(df_curr) == 0) next
  
  # D. Plot (bubble plot)
  clean_title <- gsub("_", " ", model_label)
  show_y_axis <- (i == 1)
  
  p <- ggplot(df_curr, aes(x = Target, y = Source)) + 
    coord_fixed(ratio = 1) +
    geom_tile(fill = NA, color = "grey92", linewidth = 0.5) +
    geom_point(aes(size = abs(Freq), fill = Freq), shape = 21, color = "white", stroke = 0.5) +
    scale_size_continuous(range = c(6, 18), limits = c(0, 0.5), guide = "none") + 
    
    scale_fill_gradient2(low = color_neg, mid = color_mid, high = color_pos, 
                         midpoint = 0, limits = c(-0.25, 0.25), oob = scales::squish, 
                         name = "Partial Correlation") +
    
    geom_text(aes(label = sprintf("%.2f", Freq)), size = 3, fontface = "bold", 
              color = ifelse(abs(df_curr$Freq) > 0.15, "white", "black")) +
    geom_text(data = subset(df_curr, Is_Env_Bridge), label = "★", color = color_env_bridge, size = 5, vjust = 0.5, position = position_nudge(x = -0.35, y = 0.35)) +
    geom_text(data = subset(df_curr, Is_Health_Bridge), label = "★", color = color_health_bridge, size = 5, vjust = 0.5, position = position_nudge(x = 0.35, y = 0.35)) +
    theme_minimal() +
    theme(panel.grid = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1, size = 10, color = "black", face = "bold"),
          axis.text.y = if(show_y_axis) element_text(size = 10, color = "black", face = "bold") else element_blank(),
          axis.title = element_blank(), plot.title = element_text(face = "bold", size = 13, hjust = 0.5),
          panel.border = element_rect(color = "black", fill = NA, linewidth = 0.8), legend.position = "bottom") +
    labs(title = clean_title)
  
  plot_list[[model_label]] <- p
}

# --- 3. Assemble and save ---
if (length(plot_list) > 0) {
  combined_plot <- wrap_plots(plot_list, ncol = 3) + plot_layout(guides = "collect") + 
    plot_annotation(
      title = "Figure 3: Bilateral Relationships (Bubble Matrix)",
      subtitle = "Bubble size = Magnitude; Color = Sign (Green = Positive, Red = Negative); ★ = Top 20% Bridge Node",
      theme = theme(plot.title = element_text(size = 16, face = "bold"))
    )
  out_pdf <- file.path(save_dir, "Figure3_Combined_BubbleStyle_GreenRed.pdf")
  ggsave(out_pdf, combined_plot, width = 18, height = 7)
  message(paste("Red/green bubble plot saved to:", out_pdf))
  print(combined_plot)
} else {
  message("No figure produced; check the data source.")
}



# ==============================================================================
# Final Figure 3B: bipartite network flow (sorted + green/red colour)
# ==============================================================================
# Fix: package name corrected to ggbump (all lowercase)
# ==============================================================================

# 1. Check and install (corrected package name)
if (!requireNamespace("ggbump", quietly = TRUE)) install.packages("ggbump")

# 2. Load packages
library(ggplot2)
library(dplyr)
library(tidyr)
library(patchwork)
library(here)
library(ggbump) # <--- corrected to lowercase

message("\n========== Generating the red/green sorted flow plot ==========")

# --- 1. Paths and configuration ---
source_dir <- here::here("output")
save_dir   <- here::here("plot")
if(!dir.exists(save_dir)) dir.create(save_dir, recursive = TRUE)

models <- c("Mental_Health", "Physical_Health", "Social_Health")

# Colour scheme
color_pos <- "#228B22"  # forest green (positive)
color_neg <- "#EE2C2C"  # firebrick red (negative)
color_mid <- "grey90"   # midpoint colour

bipartite_list <- list()

# --- 2. Loop over each model ---
for (i in seq_along(models)) {
  model_label <- models[i]
  
  # A. Read data
  bggm_file <- file.path(source_dir, paste0("adj_matrix_BGGM_", model_label, "_Pearson_Resid.csv"))
  if (!file.exists(bggm_file)) bggm_file <- here::here("plot", paste0("adj_matrix_BGGM_", model_label, "_Pearson_Resid.csv"))
  if (!file.exists(bggm_file)) next

  raw_data <- read.csv(bggm_file, check.names = FALSE)
  if (ncol(raw_data) <= 1) raw_data <- read.csv(bggm_file, sep = ";", check.names = FALSE)
  if (ncol(raw_data) > 1) {
    rownames(raw_data) <- raw_data[, 1]
    adj_mat <- as.matrix(raw_data[, -1])
  } else next

  # B. Extract cross-level edges
  indices <- which(adj_mat != 0, arr.ind = TRUE)
  if(nrow(indices) == 0) next
  
  df_curr <- data.frame(
    Source = rownames(adj_mat)[indices[, 1]],
    Target = colnames(adj_mat)[indices[, 2]],
    Freq   = adj_mat[indices],
    stringsAsFactors = FALSE
  ) %>%
    mutate(
      Type_From = case_when(grepl("^E", Source) ~ "E", grepl("^L", Source) ~ "L", TRUE ~ "H"),
      Type_To   = case_when(grepl("^E", Target) ~ "E", grepl("^L", Target) ~ "L", TRUE ~ "H")
    ) %>%
    filter((Type_From == "E" & Type_To == "H") | (Type_From == "H" & Type_To == "E")) %>%
    mutate(
      Real_Source = ifelse(Type_From == "E", Source, Target),
      Real_Target = ifelse(Type_To == "H", Target, Source)
    ) %>%
    select(Source = Real_Source, Target = Real_Target, Freq)

  if(nrow(df_curr) == 0) next

  # C. Sort by strength
  rank_source <- df_curr %>% group_by(Source) %>% summarise(Total_Weight = sum(abs(Freq))) %>% arrange(desc(Total_Weight))
  rank_target <- df_curr %>% group_by(Target) %>% summarise(Total_Weight = sum(abs(Freq))) %>% arrange(desc(Total_Weight))
  
  sorted_sources <- rank_source$Source
  sorted_targets <- rank_target$Target
  
  # Assign Y coordinates
  df_nodes_source <- data.frame(
    Label = sorted_sources, x = 0, 
    y = if(length(sorted_sources)>1) seq(0.9, 0.1, length.out = length(sorted_sources)) else 0.5
  )
  df_nodes_target <- data.frame(
    Label = sorted_targets, x = 1, 
    y = if(length(sorted_targets)>1) seq(0.9, 0.1, length.out = length(sorted_targets)) else 0.5
  )
  
  # Merge coordinates
  df_flow <- df_curr %>%
    left_join(df_nodes_source, by = c("Source" = "Label")) %>% rename(x_start = x, y_start = y) %>%
    left_join(df_nodes_target, by = c("Target" = "Label")) %>% rename(x_end = x, y_end = y)
  
  p_flow <- ggplot() +
    # sigmoid curve
    ggbump::geom_sigmoid(data = df_flow, 
                         aes(x = x_start + 0.02, y = y_start, xend = x_end - 0.02, yend = y_end, 
                             color = Freq, linewidth = abs(Freq)),
                         alpha = 0.8, smooth = 8, direction = "x") +
    # nodes
    geom_point(data = df_nodes_source, aes(x = x, y = y), size = 5, shape = 21, fill = "white", color = "black", stroke = 0.8) +
    geom_point(data = df_nodes_target, aes(x = x, y = y), size = 5, shape = 21, fill = "white", color = "black", stroke = 0.8) +
    # Labels
    geom_text(data = df_nodes_source, aes(x = x - 0.05, y = y, label = Label), hjust = 1, size = 3.2, fontface = "bold") +
    geom_text(data = df_nodes_target, aes(x = x + 0.05, y = y, label = Label), hjust = 0, size = 3.2, fontface = "bold") +
    # values
    geom_text(data = df_flow, 
              aes(x = (x_start + x_end)/2, y = (y_start + y_end)/2 + 0.02, 
                  label = sprintf("%.2f", Freq), color = Freq), 
              size = 2.5, fontface = "bold", check_overlap = TRUE, show.legend = FALSE) +
    
    # red/green colours
    scale_color_gradient2(low = color_neg, mid = color_mid, high = color_pos, 
                          limits = c(-0.25, 0.25), name = "Partial Corr.") +
    scale_linewidth(range = c(0.8, 4), guide = "none") +
    
    xlim(-0.4, 1.4) + ylim(-0.05, 1.05) + 
    labs(title = gsub("_", " ", model_label)) +
    theme_void() +
    theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5, face = "bold", margin = margin(b = 10)), plot.margin = margin(t = 20, b = 10))

  bipartite_list[[model_label]] <- p_flow
}

# --- 3. Assemble and save ---
if (length(bipartite_list) > 0) {
  
  # 1. Combine the panels
  p_combined_flow <- wrap_plots(bipartite_list, ncol = 3) + 
    plot_layout(guides = "collect") +
    plot_annotation(
      title = "Figure 3B: Bipartite Network Flow (Sorted by Strength)",
      subtitle = "Nodes ordered by total strength. Color indicates sign (Green = Positive, Red = Negative).",
      theme = theme(
        plot.title = element_text(size = 16, face = "bold"),
        plot.subtitle = element_text(size = 11, color = "gray30")
      )
    )
  
  # 2. Set the save path
  out_pdf <- file.path(save_dir, "Figure3B_Bipartite_Flow_Sorted_GreenRed.pdf")
  
  # 3. Save
  ggsave(out_pdf, p_combined_flow, width = 18, height = 8)
  
  message(paste("Red/green flow plot saved to:", out_pdf))
  print(p_combined_flow)
  
} else {
  message("No figure produced; check the data source.")
}

# ==============================================================================
# Figure 3B: bipartite Sankey / alluvial flow plot
# ==============================================================================
# Core design:
# 1. Follow the Sankey style of Figure 4 (ggalluvial).
# 2. Left stratum = environment factors (E); right stratum = health factors (H).
# 3. Bar height = sum of all edge strengths at that node (reflects "volume").
# 4. Band colour: red = negative, green = positive.
# ==============================================================================

# 1. Check and install ggalluvial
if (!requireNamespace("ggalluvial", quietly = TRUE)) install.packages("ggalluvial")

library(ggplot2)
library(dplyr)
library(tidyr)
library(here)
library(ggalluvial) # core plotting package

message("\n========== Generating Figure 3B (Sankey style) ==========")

# --- 1. Paths and configuration ---
source_dir <- here::here("output")
save_dir   <- here::here("plot")
if(!dir.exists(save_dir)) dir.create(save_dir, recursive = TRUE)

models <- c("Mental_Health", "Physical_Health", "Social_Health")

# Colours: red = negative, green = positive
color_pos <- "#228B22"  # Forest Green
color_neg <- "#EE2C2C"  # Firebrick Red

plot_list <- list()

# --- 2. Loop over each model ---
for (model_label in models) {
  
  # A. Read data
  bggm_file <- file.path(source_dir, paste0("adj_matrix_BGGM_", model_label, "_Pearson_Resid.csv"))
  if (!file.exists(bggm_file)) bggm_file <- here::here("plot", paste0("adj_matrix_BGGM_", model_label, "_Pearson_Resid.csv"))
  if (!file.exists(bggm_file)) next

  raw_data <- read.csv(bggm_file, check.names = FALSE)
  if (ncol(raw_data) <= 1) raw_data <- read.csv(bggm_file, sep = ";", check.names = FALSE)
  if (ncol(raw_data) > 1) {
    rownames(raw_data) <- raw_data[, 1]
    adj_mat <- as.matrix(raw_data[, -1])
  } else next

  # B. Extract cross-level edges (E <-> H)
  indices <- which(adj_mat != 0, arr.ind = TRUE)
  if(nrow(indices) == 0) next
  
  df_curr <- data.frame(
    Source = rownames(adj_mat)[indices[, 1]],
    Target = colnames(adj_mat)[indices[, 2]],
    Freq   = adj_mat[indices],
    stringsAsFactors = FALSE
  ) %>%
    mutate(
      Type_From = case_when(grepl("^E", Source) ~ "E", grepl("^L", Source) ~ "L", TRUE ~ "H"),
      Type_To   = case_when(grepl("^E", Target) ~ "E", grepl("^L", Target) ~ "L", TRUE ~ "H")
    ) %>%
    filter((Type_From == "E" & Type_To == "H") | (Type_From == "H" & Type_To == "E")) %>%
    mutate(
      Real_Source = ifelse(Type_From == "E", Source, Target),
      Real_Target = ifelse(Type_To == "H", Target, Source)
    ) %>%
    select(Source = Real_Source, Target = Real_Target, Freq) %>%
    # add sign labels for fill colour
    mutate(
      Direction = ifelse(Freq > 0, "Positive (+)", "Negative (-)"),
      Abs_Freq  = abs(Freq) # used for width mapping
    )

  if(nrow(df_curr) == 0) next

  # C. Plot (using ggalluvial)
  # ---------------------------------------------------------
  clean_title <- gsub("_", " ", model_label)
  
  p <- ggplot(df_curr,
              aes(axis1 = Source, axis2 = Target, y = Abs_Freq)) + # y maps to the absolute value, driving bar height
    
    # 1. Flow layer (alluvium)
    geom_alluvium(aes(fill = Direction), 
                  width = 1/6,       # stratum width
                  alpha = 0.7,       # transparency (the desired overlay effect)
                  curve_type = "sigmoid") + # smooth sigmoid curve
    
    # 2. Stratum layer - bar height equals the aggregated volume
    geom_stratum(width = 1/6, fill = "grey95", color = "grey30") +
    
    # 3. Text labels
    geom_text(stat = "stratum", aes(label = after_stat(stratum)), 
              size = 3, fontface = "bold") +
    
    # 4. Style settings
    scale_x_discrete(limits = c("Environment", "Health Outcome"), expand = c(0.1, 0.1)) +
    scale_fill_manual(values = c("Positive (+)" = color_pos, "Negative (-)" = color_neg)) +
    
    labs(title = clean_title, 
         y = "Total Connection Strength (|r| sum)", 
         fill = "Correlation") +
    
    theme_minimal() +
    theme(
      panel.grid = element_blank(),
      axis.text.y = element_blank(), # hide Y ticks; only relative height matters
      axis.ticks = element_blank(),
      axis.text.x = element_text(size = 12, face = "bold", color = "black"),
      plot.title = element_text(hjust = 0.5, face = "bold"),
      legend.position = "bottom"
    )

  plot_list[[model_label]] <- p
}

# --- 3. Assemble and save ---
if (length(plot_list) > 0) {
  
  library(patchwork)
  
  # 1. Combine the panels
  p_combined <- wrap_plots(plot_list, ncol = 3) + 
    plot_layout(guides = "collect") +
    plot_annotation(
      title = "Figure 3B: Bipartite Network Flow (Sankey Style)",
      subtitle = "Bar height represents total connection strength. Band width represents individual correlation magnitude.",
      theme = theme(
        plot.title = element_text(size = 16, face = "bold"),
        legend.position = "bottom" # set the legend position here
      )
    )
  
  # 2. Save
  out_pdf <- file.path(save_dir, "Figure3B_Bipartite_Sankey.pdf")
  ggsave(out_pdf, p_combined, width = 18, height = 8)
  
  message(paste("Sankey-style bipartite plot saved to:", out_pdf))
  print(p_combined)
  
} else {
  message("No figure produced; check the data source.")
}

```


```{r}

# ==============================================================================
# 3. Figure 6: DAG summary (reads RDS directly)
# ==============================================================================
message("\n========== Generating Figure 6 (DAG summary) ==========")

list_dag_summary <- list()

for (model_label in models) {
  bggm_file <- file.path(out_dir, paste0("adj_matrix_BGGM_", model_label, "_Pearson_Resid.csv"))
  if (!file.exists(bggm_file)) next
  adj_mat <- as.matrix(read.csv(bggm_file, row.names = 1))
  
  edges_bggm <- as.data.frame(as.table(adj_mat)) %>%
    filter(Freq != 0, abs(Freq) > 0.02) %>%
    rename(Node1 = Var1, Node2 = Var2) %>%
    mutate(
      Type1 = case_when(grepl("^E", Node1)~"E", grepl("^L", Node1)~"L", grepl("^[MPS]", Node1)~"H", TRUE~"O"),
      Type2 = case_when(grepl("^E", Node2)~"E", grepl("^L", Node2)~"L", grepl("^[MPS]", Node2)~"H", TRUE~"O")
    ) %>%
    rowwise() %>%
    mutate(Key = paste(sort(c(as.character(Node1), as.character(Node2))), collapse = "|")) %>%
    ungroup() %>% distinct(Key, .keep_all = TRUE)
  
  # --- Key change: read the RDS ---
  rds_file <- file.path(out_dir_dag, paste0("Boot_Object_", model_label, ".rds"))
  dag_keys <- character()
  
  if (file.exists(rds_file)) {
    str_fit <- readRDS(rds_file)
    avg_dag <- averaged.network(str_fit, threshold = DAG_THRESHOLD)
    dag_arcs <- as.data.frame(avg_dag$arcs)
    if(nrow(dag_arcs) > 0){
      from_safe <- make.names(dag_arcs$from)
      to_safe   <- make.names(dag_arcs$to)
      dag_keys  <- paste0(from_safe, "->", to_safe)
    }
  }

classify_edge <- function(n1, n2, t1, t2) {
      s1 <- make.names(n1)
    s2 <- make.names(n2)

    if(setequal(c(t1,t2), c("E","L"))) { 
      p="E-L"; 
      exp=paste0(ifelse(t1=="E",s1,s2),"->",ifelse(t1=="L",s1,s2)); 
      rev=paste0(ifelse(t1=="L",s1,s2),"->",ifelse(t1=="E",s1,s2)) 
    }
    else if(setequal(c(t1,t2), c("L","H"))) { 
      p="L-H"; 
      exp=paste0(ifelse(t1=="L",s1,s2),"->",ifelse(t1=="H",s1,s2)); 
      rev=paste0(ifelse(t1=="H",s1,s2),"->",ifelse(t1=="L",s1,s2)) 
    }
    else if(setequal(c(t1,t2), c("E","H"))) { 
      p="E-H"; 
      exp=paste0(ifelse(t1=="E",s1,s2),"->",ifelse(t1=="H",s1,s2)); 
      rev=paste0(ifelse(t1=="H",s1,s2),"->",ifelse(t1=="E",s1,s2)) 
    }
    else return(NULL)
    
    stat <- "Undirected (BGGM Only)"
    if(exp %in% dag_keys) stat <- "Directed (Expected)"
    else if(rev %in% dag_keys) stat <- "Directed (Reverse)"
    return(data.frame(Domain=p, Status=stat))
}

  res_list <- list()
  for(i in 1:nrow(edges_bggm)) res_list[[i]] <- classify_edge(as.character(edges_bggm$Node1[i]), as.character(edges_bggm$Node2[i]), edges_bggm$Type1[i], edges_bggm$Type2[i])
  df_sum <- bind_rows(res_list)
  if(nrow(df_sum)>0) { df_sum$Model <- model_label; list_dag_summary[[model_label]] <- df_sum }
}

df_fig6 <- bind_rows(list_dag_summary)
if(nrow(df_fig6)>0) {
  p6 <- ggplot(df_fig6, aes(x=Domain, fill=Status)) +
    geom_bar(position="stack", width=0.6) +
    geom_text(stat='count', aes(label=after_stat(count)), position=position_stack(vjust=0.5), color="white", size=3) +
    facet_wrap(~Model, scales="free_y") +
    scale_fill_manual(values=c("Directed (Expected)"="#2E8B57", "Directed (Reverse)"="#CD5C5C", "Undirected (BGGM Only)"="#A9A9A9")) +
    labs(title="Figure 6: Summary of Causal Directions", subtitle=paste0("Threshold: ", DAG_THRESHOLD, " (RDS Source)"), x="Domain Pair", y="Edge Count") +
    theme_minimal() + theme(legend.position="bottom")
  
  ggsave(file.path(out_dir, "Figure6_DAG_Summary.pdf"), p6, width=12, height=8)
  print(p6)
  message("Figure 6 complete.")
}

# ==============================================================================
# 4. Figure 4: indirect pathways (reads RDS directly)
# ==============================================================================
message("\n========== Generating Figure 4 (indirect pathways) ==========")

list_indirect <- list()

for (model_label in models) {
  bggm_file <- file.path(out_dir, paste0("adj_matrix_BGGM_", model_label, "_Pearson_Resid.csv"))
  if (!file.exists(bggm_file)) next
  adj_mat <- as.matrix(read.csv(bggm_file, row.names = 1))
  
  # --- Key change: read the RDS ---
  rds_file <- file.path(out_dir_dag, paste0("Boot_Object_", model_label, ".rds"))
  dag_keys <- character()
  
  if (file.exists(rds_file)) {
    str_fit <- readRDS(rds_file)
    avg_dag <- averaged.network(str_fit, threshold = DAG_THRESHOLD)
    dag_arcs <- as.data.frame(avg_dag$arcs)
    if(nrow(dag_arcs) > 0){
      from_safe <- make.names(dag_arcs$from)
      to_safe   <- make.names(dag_arcs$to)
      dag_keys  <- paste0(from_safe, "->", to_safe)
    }
  }
  
  # Build the base edge list
  edges_bggm <- as.data.frame(as.table(adj_mat)) %>%
    filter(Freq != 0, abs(Freq) > 0.00) %>%
    mutate(Strength = abs(Freq)) %>%
    mutate(
      Type1 = case_when(grepl("^E", Var1)~"E", grepl("^L", Var1)~"L", grepl("^[MPS]", Var1)~"H", TRUE~"Other"),
      Type2 = case_when(grepl("^E", Var2)~"E", grepl("^L", Var2)~"L", grepl("^[MPS]", Var2)~"H", TRUE~"Other"))

path_EL <- edges_bggm %>%
    filter((Type1 == "E" & Type2 == "L") | (Type1 == "L" & Type2 == "E")) %>%
    mutate(S = ifelse(Type1=="E", as.character(Var1), as.character(Var2)),
           T = ifelse(Type1=="L", as.character(Var1), as.character(Var2)),
           Key = paste0(make.names(S), "->", make.names(T))) %>%  
    select(S, T, Strength, Key) %>% rename(E=S, L=T, Str1=Strength, Key1=Key)

path_LH <- edges_bggm %>%
    filter((Type1 == "L" & Type2 == "H") | (Type1 == "H" & Type2 == "L")) %>%
    mutate(S = ifelse(Type1=="L", as.character(Var1), as.character(Var2)),
           T = ifelse(Type1=="H", as.character(Var1), as.character(Var2)),
           # apply make.names
           Key = paste0(make.names(S), "->", make.names(T))) %>% 
    select(S, T, Strength, Key) %>% rename(L=S, H=T, Str2=Strength, Key2=Key)
  
  full_path <- inner_join(path_EL, path_LH, by = "L") %>%
    mutate(
      Conf1 = Key1 %in% dag_keys,
      Conf2 = Key2 %in% dag_keys,
      Validation = case_when(
        Conf1 & Conf2 ~ "Strong Chain (Both Steps DAG Verified)",
        Conf1 | Conf2 ~ "Partial Chain (One Step DAG Verified)",
        TRUE ~ "Associational Chain (BGGM Only)"),
      
      Width = (Str1 + Str2)/2,
      Model = model_label
    )
  list_indirect[[model_label]] <- full_path
}

df_indirect <- bind_rows(list_indirect)

if (nrow(df_indirect) > 0) {
  df_indirect_viz <- df_indirect %>% filter(Width > 0.00) 
  
  if(nrow(df_indirect_viz) > 0) {
    p4 <- ggplot(df_indirect_viz, aes(axis1 = E, axis2 = L, axis3 = H, y = Width)) +
      geom_alluvium(aes(fill = Validation), width = 1/12, alpha = 0.8) +
      geom_stratum(width = 1/6, fill = "grey95", color = "grey20") +
      geom_text(stat = "stratum", aes(label = after_stat(stratum)), size = 2.5) +
      scale_x_discrete(limits = c("Environment", "Lifestyle Mediator", "Health Outcome"), expand = c(.05, .05)) +
      scale_fill_manual(values = c("Strong Chain (Both Steps DAG Verified)"="#2E8B57", 
                                   "Partial Chain (One Step DAG Verified)"="#EEB422", 
                                   "Associational Chain (BGGM Only)"="#B0C4DE")) +
      facet_wrap(~Model, scales = "free") +
      labs(title = "Figure 4: Indirect Pathways (E->L->H)", 
           subtitle = paste0("Threshold: ", DAG_THRESHOLD, " (RDS Source)"),
           fill = "Causal Evidence") +
      theme_void() + theme(legend.position = "bottom", strip.text = element_text(face="bold"))
    
    ggsave(file.path(out_dir, "Figure4_Indirect_Alluvial.pdf"), p4, width = 16, height = 10)
    print(p4)
    message("Figure 4 complete.")
  }
} else {
  message("Figure 4 not produced: no qualifying pathways found.")
}

message("\nAll figures updated; direct-RDS mode complete.")
```

